---
title: "Berlin CO2 Emissionen (2002- 2018)"
author: "Bhaskar Kamble"
date: "3 Juli 2019"
output: 
  beamer_presentation:    
    includes:
      in_header: D:/GITHUB_REPOS/co2emissions/Berlin/BezirkAnalysis/header_pagenrs.tex
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=FALSE,message=FALSE,warning=FALSE)
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
source("D:/GITHUB_REPOS/co2emissions/Berlin/mainCO2_Berlin.R")
et_list <- c("erdgas","fluessiggas","heizoel","holzpellets","strom","waerme")

sfh_data <- main_function("SFH" , et_list)
mfh_data <- main_function("MFH" , et_list)
co2_SFH <- sfh_data$co2_emissions#main_function("SFH" , et_list)
co2_MFH <- mfh_data$co2_emissions#main_function("MFH" , et_list)
co2_ALL <- co2_SFH + co2_MFH
co2_ALL$abrechnungsjahr <- 2002:2018
co2_SFH <- co2_SFH/1e9 # in kilo tons
co2_MFH <- co2_MFH/1e9 # in kilo tons
co2_ALL <- co2_ALL/1e9 # in kilo tons
co2_SFH$abrechnungsjahr <- 2002:2018
co2_MFH$abrechnungsjahr <- 2002:2018
co2_ALL$abrechnungsjahr <- 2002:2018
```

```{r}
#co2_MFH
#co2_SFH
```

```{r}
# You must impute average value of CO2 emissions for Strom for the period 2002-2009.
# Ideally you must impute these missing values to the energy consumption and area covered by Strom in the period 2002-2009.
# anyway do it for co2 emissions now.
# 1. Modify CO2_SFH
# 2. Modify CO2_MFH
# Add them to get CO2_ALL like you did in the first code chunk.
co2_SFH$strom[co2_SFH$abrechnungsjahr < 2010] <- mean(co2_SFH$strom[co2_SFH$abrechnungsjahr >2009])
co2_MFH$strom[co2_MFH$abrechnungsjahr < 2010] <- mean(co2_MFH$strom[co2_MFH$abrechnungsjahr >2009])
co2_ALL <- co2_SFH + co2_MFH
co2_ALL$abrechnungsjahr <- 2002:2018
co2_SFH <- getRowSums(co2_SFH[ , names(co2_SFH)!="total"] , dropCols = "abrechnungsjahr")
co2_MFH <- getRowSums(co2_MFH[ , names(co2_MFH)!="total"] , dropCols = "abrechnungsjahr")
co2_ALL <- getRowSums(co2_ALL[ , names(co2_ALL)!="total"] , dropCols = "abrechnungsjahr")
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
co2_MFH_rel <- find_proportions(co2_MFH , c("abrechnungsjahr" , "total"))
co2_MFH_rel <- getRowSums(co2_MFH_rel , "abrechnungsjahr")
co2_SFH_rel <- find_proportions(co2_SFH , c("abrechnungsjahr" , "total"))
co2_SFH_rel <- getRowSums(co2_SFH_rel , "abrechnungsjahr")
co2_ALL_rel <- find_proportions(co2_ALL , c("abrechnungsjahr" , "total"))
co2_ALL_rel <- getRowSums(co2_ALL_rel , "abrechnungsjahr")
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
source("D:/GITHUB_REPOS/co2emissions/Berlin/BezirkAnalysis/getCumSums.R")
co2_SFH_cumsums <- getCumSums(co2_SFH , c("abrechnungsjahr","total"))
co2_MFH_cumsums <- getCumSums(co2_MFH , c("abrechnungsjahr","total"))
co2_ALL_cumsums <- getCumSums(co2_ALL , c("abrechnungsjahr","total"))
co2_SFH_rel_cumsums <- getCumSums(co2_SFH_rel , c("abrechnungsjahr","total"))
co2_MFH_rel_cumsums <- getCumSums(co2_MFH_rel , c("abrechnungsjahr","total"))
co2_ALL_rel_cumsums <- getCumSums(co2_ALL_rel , c("abrechnungsjahr","total"))
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
et_list <- names(co2_SFH)[!(names(co2_SFH) %in% c("abrechnungsjahr","total"))]
col_list <- c("royalblue4","orangered1","gray59","orange","blue","olivedrab4")
cols <- c(
          "erdgas"      = "royalblue4",
          "waerme"      = "orangered1",
          "fluessiggas" = "gray59",
          "heizoel"     = "orange",
          "holzpellets" = "blue",
          "strom"       = "olivedrab4"
          )
plot_title <- NULL
order_legend <- rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
order_labels <- rev(c("Erdgas","Wärme (N+F)","Flüssiggas","Heizöl","Holzpellets","Strom (D+WP)"))
```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
require(ggplot2)
plot_byET <- function(obj,xlabel,ylabel,plottitle) {
  ggplot()+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1]),size=5
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
  )+scale_color_manual(labels=order_labels,name=" ",values=cols,breaks=order_legend
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1])+theme_bw()+ labs(x=xlabel,y=ylabel,title=plottitle) + theme(plot.title=element_text(size=30), axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"), legend.key.size=unit(2, "lines")
  )+scale_x_continuous(breaks=seq(2002,2018,2))
}
```



```{r}
linearizer <- function(obj,dropCols,xVar) {
  obj_new <- obj[ , !(names(obj) %in% dropCols)]
  feature_list <- names(obj_new)[ !(names(obj_new) %in% c(dropCols,xVar)) ]
  storage <- list()
  for (feature in feature_list) {
    storage[[feature]] <- lm(get(feature) ~ get(xVar) , data = obj)
    obj_new[[feature]] <- as.numeric(predict(storage[[feature]] , newdata = obj))
  }
  return(obj_new)
}

#getMissingStrom <- function(obj , missingYears) {
#  lin_Strom <- lm(strom ~ abrechnungsjahr , data = obj)
#  appendData <- data.frame(abrechnungsjahr = missingYears)
#  appendData$strom <- predict(lin_Strom , newdata = appendData)
#  return(rbind(appendData , obj))
#}

cap100 <- function(obj) {
  etcols <- names(obj)[names(obj)!="abrechnungsjahr"]
  for (e in etcols) {
    obj[[e]][obj[[e]]>100] <- 100
  }
  return(obj)
}
```


\textcolor{black}{Berlin, 1-2 Familiengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
co2_SFH_linear <- linearizer(co2_SFH,"total","abrechnungsjahr")
co2_SFH_linear_cumsums <- getCumSums(co2_SFH_linear , "abrechnungsjahr")
plot_byET(co2_SFH_linear_cumsums , "Jahr" , "kilo t." , NULL)
```


***********


\textcolor{black}{Berlin, 1-2 Familiengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
co2_SFH_linear_rel <- find_proportions(co2_SFH_linear , "abrechnungsjahr")
co2_SFH_linear_rel_cumsums <- getCumSums(co2_SFH_linear_rel , "abrechnungsjahr")
co2_SFH_linear_rel_cumsums <- cap100(co2_SFH_linear_rel_cumsums)
plot_byET(co2_SFH_linear_rel_cumsums , "Jahr" , "Anteile" , NULL)
```

************


\textcolor{black}{Berlin, 1-2 Familiengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}



```{r}
co2_SFH_lintrend <- co2_SFH[, c("abrechnungsjahr","total")]
lin_co2 <- lm(total~abrechnungsjahr , data = co2_SFH)
co2_SFH_lintrend$total <- predict(lin_co2 , newdata = co2_SFH_lintrend)
b0 <- round(as.numeric(lin_co2$coefficients[1]),0)
b1 <- round(as.numeric(lin_co2$coefficients[2]),2)
ggplot()+geom_line(data=co2_SFH_lintrend,aes(x=abrechnungsjahr,y=total),size=2)+scale_y_continuous(limits=c(0,1300))+annotate(geom="text",label=paste0(b1,"x"," + ", b0),x=2008,y=1150,size=6)+theme_bw()+labs(x="Jahr",y="kilo t.")+theme(axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"))+scale_x_continuous(breaks=seq(2002,2018,2))


```

************


\textcolor{black}{Berlin, Mehrfamiliengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
co2_MFH_linear <- linearizer(co2_MFH, dropCols = "total", xVar = "abrechnungsjahr")
co2_MFH_linear_cumsums <- getCumSums(co2_MFH_linear , "abrechnungsjahr")
plot_byET(co2_MFH_linear_cumsums , "Jahr" , "kilo t." , NULL)
```


************

\textcolor{black}{Berlin, Mehrfamiliengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
co2_MFH_linear_rel <- find_proportions(co2_MFH_linear , "abrechnungsjahr")
co2_MFH_linear_rel_cumsums <- getCumSums(co2_MFH_linear_rel , "abrechnungsjahr")
co2_MFH_linear_rel_cumsums <- cap100(co2_MFH_linear_rel_cumsums)
plot_byET(co2_MFH_linear_rel_cumsums , "Jahr" , "Anteile" , NULL)
```



************

\textcolor{black}{Berlin, Mehrfamiliengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}



```{r}
co2_MFH_lintrend <- co2_MFH[, c("abrechnungsjahr","total")]
lin_co2 <- lm(total~abrechnungsjahr , data = co2_MFH)
co2_MFH_lintrend$total <- predict(lin_co2 , newdata = co2_MFH_lintrend)
b0 <- round(as.numeric(lin_co2$coefficients[1]),0)
b1 <- round(as.numeric(lin_co2$coefficients[2]),2)
ggplot()+geom_line(data=co2_MFH_lintrend,aes(x=abrechnungsjahr,y=total),size=2)+scale_y_continuous(limits=c(0,max(co2_MFH_lintrend$total)))+annotate(geom="text",label=paste0(b1,"x"," + ", b0),x=2008,y=3500,size=6)+theme_bw()+labs(x="Jahr",y="kilo t.")+theme(axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"))+scale_x_continuous(breaks=seq(2002,2018,2))


```










************

\textcolor{black}{Berlin, Wohngebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
co2_ALL_linear <- linearizer(co2_ALL, dropCols = "total", xVar = "abrechnungsjahr")
co2_ALL_linear_cumsums <- getCumSums(co2_ALL_linear , "abrechnungsjahr")
plot_byET(co2_ALL_linear_cumsums , "Jahr" , "kilo t." , NULL)
```


************

\textcolor{black}{Berlin, Wohngebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
co2_ALL_linear_rel <- find_proportions(co2_ALL_linear , "abrechnungsjahr")
co2_ALL_linear_rel_cumsums <- getCumSums(co2_ALL_linear_rel , "abrechnungsjahr")
co2_ALL_linear_rel_cumsums <- cap100(co2_ALL_linear_rel_cumsums)
plot_byET(co2_ALL_linear_rel_cumsums , "Jahr" , "Anteile" , NULL)
```



************

\textcolor{black}{Berlin, Wohngebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}



```{r}
co2_ALL_lintrend <- co2_ALL[, c("abrechnungsjahr","total")]
lin_co2 <- lm(total~abrechnungsjahr , data = co2_ALL)
co2_ALL_lintrend$total <- predict(lin_co2 , newdata = co2_ALL_lintrend)
b0 <- round(as.numeric(lin_co2$coefficients[1]),0)
b1 <- round(as.numeric(lin_co2$coefficients[2]),2)
ggplot()+geom_line(data=co2_ALL_lintrend,aes(x=abrechnungsjahr,y=total),size=2)+scale_y_continuous(limits=c(0,max(co2_ALL_lintrend$total)))+annotate(geom="text",label=paste0(b1,"x"," + ", b0),x=2008,y=4500,size=6)+theme_bw()+labs(x="Jahr",y="kilo t.")+theme(axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"))+scale_x_continuous(breaks=seq(2002,2018,2))


```




