---
title: "Berlin CO2 Emissionen (2002- 2018)"
author: "Bhaskar Kamble"
date: "3 Juli 2019"
output: 
  beamer_presentation:    
    includes:
      in_header: D:/GITHUB_REPOS/co2emissions/Berlin/BezirkAnalysis/header_pagenrs.tex
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=FALSE,message=FALSE,warning=FALSE)
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
source("D:/GITHUB_REPOS/co2emissions/Berlin/mainCO2_Berlin.R")
et_list <- c("erdgas","fluessiggas","heizoel","holzpellets","strom","waerme")

sfh_data <- main_function("SFH" , et_list)
mfh_data <- main_function("MFH" , et_list)
co2_SFH <- sfh_data$co2_emissions#main_function("SFH" , et_list)
co2_MFH <- mfh_data$co2_emissions#main_function("MFH" , et_list)
co2_ALL <- co2_SFH + co2_MFH
co2_ALL$abrechnungsjahr <- 2002:2018
co2_SFH <- co2_SFH/1e9 # in kilo tons
co2_MFH <- co2_MFH/1e9 # in kilo tons
co2_ALL <- co2_ALL/1e9 # in kilo tons
co2_SFH$abrechnungsjahr <- 2002:2018
co2_MFH$abrechnungsjahr <- 2002:2018
co2_ALL$abrechnungsjahr <- 2002:2018
```

```{r}
#co2_MFH
#co2_SFH
```

```{r}
# You must impute average value of CO2 emissions for Strom for the period 2002-2009.
# Ideally you must impute these missing values to the energy consumption and area covered by Strom in the period 2002-2009.
# anyway do it for co2 emissions now.
# 1. Modify CO2_SFH
# 2. Modify CO2_MFH
# Add them to get CO2_ALL like you did in the first code chunk.
co2_SFH$strom[co2_SFH$abrechnungsjahr < 2010] <- mean(co2_SFH$strom[co2_SFH$abrechnungsjahr >2009])
co2_MFH$strom[co2_MFH$abrechnungsjahr < 2010] <- mean(co2_MFH$strom[co2_MFH$abrechnungsjahr >2009])
co2_ALL <- co2_SFH + co2_MFH
co2_ALL$abrechnungsjahr <- 2002:2018
co2_SFH <- getRowSums(co2_SFH[ , names(co2_SFH)!="total"] , dropCols = "abrechnungsjahr")
co2_MFH <- getRowSums(co2_MFH[ , names(co2_MFH)!="total"] , dropCols = "abrechnungsjahr")
co2_ALL <- getRowSums(co2_ALL[ , names(co2_ALL)!="total"] , dropCols = "abrechnungsjahr")
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
co2_MFH_rel <- find_proportions(co2_MFH , c("abrechnungsjahr" , "total"))
co2_MFH_rel <- getRowSums(co2_MFH_rel , "abrechnungsjahr")
co2_SFH_rel <- find_proportions(co2_SFH , c("abrechnungsjahr" , "total"))
co2_SFH_rel <- getRowSums(co2_SFH_rel , "abrechnungsjahr")
co2_ALL_rel <- find_proportions(co2_ALL , c("abrechnungsjahr" , "total"))
co2_ALL_rel <- getRowSums(co2_ALL_rel , "abrechnungsjahr")
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
source("D:/GITHUB_REPOS/co2emissions/Berlin/BezirkAnalysis/getCumSums.R")
co2_SFH_cumsums <- getCumSums(co2_SFH , c("abrechnungsjahr","total"))
co2_MFH_cumsums <- getCumSums(co2_MFH , c("abrechnungsjahr","total"))
co2_ALL_cumsums <- getCumSums(co2_ALL , c("abrechnungsjahr","total"))
co2_SFH_rel_cumsums <- getCumSums(co2_SFH_rel , c("abrechnungsjahr","total"))
co2_MFH_rel_cumsums <- getCumSums(co2_MFH_rel , c("abrechnungsjahr","total"))
co2_ALL_rel_cumsums <- getCumSums(co2_ALL_rel , c("abrechnungsjahr","total"))
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
et_list <- names(co2_SFH)[!(names(co2_SFH) %in% c("abrechnungsjahr","total"))]
col_list <- c("royalblue4","orangered1","gray59","orange","blue","olivedrab4")
cols <- c(
          "erdgas"      = "royalblue4",
          "waerme"      = "orangered1",
          "fluessiggas" = "gray59",
          "heizoel"     = "orange",
          "holzpellets" = "blue",
          "strom"       = "olivedrab4"
          )
plot_title <- NULL
order_legend <- rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
order_labels <- rev(c("Erdgas","Wärme (N+F)","Flüssiggas","Heizöl","Holzpellets","Strom (D+WP)"))
```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
require(ggplot2)
plot_byET <- function(obj,xlabel,ylabel,plottitle) {
  ggplot()+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1]),size=5
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
  )+scale_color_manual(labels=order_labels,name=" ",values=cols,breaks=order_legend
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1])+theme_bw()+ labs(x=xlabel,y=ylabel,title=plottitle) + theme(plot.title=element_text(size=30), axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"), legend.key.size=unit(2, "lines")
  )+scale_x_continuous(breaks=seq(2002,2018,2))
}
```


```{r}
require(FNN)
approximate_by_kNN <- function(obj,no_of_neighbors,year_grid) {
  #obj is the data frame of the cumulative co2 emissions (absolute or relative)
  obj_new <- data.frame(abrechnungsjahr=year_grid)
  for (e in names(obj)[names(obj)!="abrechnungsjahr"]) {
    knnr.out <- knn.reg(train=obj$abrechnungsjahr , test=data.frame(abrechnungsjahr=year_grid) , y=obj[[e]] , k=no_of_neighbors)
    #in the above, test can be a finer grid of the abrechnungsjahr (2002 to 2018 in steps of 0.01, for example). 
    #This is the year_grid argument
    #e is looped over the energietraegers
    obj_new[[e]] <- knnr.out$pred
  }
  return(obj_new)
}
neighbors <- 3
```







\textcolor{black}{Berlin, 1-2 Familiengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_SFH_cumsums , "Jahr" , "kilo t." , NULL)
plot_byET(approximate_by_kNN(co2_SFH_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```


***********

\textcolor{black}{Berlin, 1-2 Familiengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_SFH_rel_cumsums , "Jahr" , "Anteile" , NULL)
plot_byET(approximate_by_kNN(co2_SFH_rel_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```


************

\textcolor{black}{Berlin, 1-2 Familiengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}



```{r}
co2_SFH_lintrend <- co2_SFH[, c("abrechnungsjahr","total")]
lin_co2 <- lm(total~abrechnungsjahr , data = co2_SFH)
co2_SFH_lintrend$total <- predict(lin_co2 , newdata = co2_SFH_lintrend)
b0 <- round(as.numeric(lin_co2$coefficients[1]),0)
b1 <- round(as.numeric(lin_co2$coefficients[2]),2)
ggplot()+geom_line(data=co2_SFH_lintrend,aes(x=abrechnungsjahr,y=total),size=2)+scale_y_continuous(limits=c(0,1300))+annotate(geom="text",label=paste0(b1,"x"," + ", b0),x=2008,y=1150,size=6)+theme_bw()+labs(x="Jahr",y="kilo t.")+theme(axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"))+scale_x_continuous(breaks=seq(2002,2018,2))


```


************

\textcolor{black}{Berlin, Mehrfamiliengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_MFH_cumsums , "Jahr" , "kilo t." , NULL)
plot_byET(approximate_by_kNN(co2_MFH_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```


************

\textcolor{black}{Berlin, Mehrfamiliengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_MFH_rel_cumsums , "Jahr" , "Anteile" , NULL)
plot_byET(approximate_by_kNN(co2_MFH_rel_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```


************

\textcolor{black}{Berlin, Mehrfamiliengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}



```{r}
co2_MFH_lintrend <- co2_MFH[, c("abrechnungsjahr","total")]
lin_co2 <- lm(total~abrechnungsjahr , data = co2_MFH)
co2_MFH_lintrend$total <- predict(lin_co2 , newdata = co2_MFH_lintrend)
b0 <- round(as.numeric(lin_co2$coefficients[1]),0)
b1 <- round(as.numeric(lin_co2$coefficients[2]),2)
ggplot()+geom_line(data=co2_MFH_lintrend,aes(x=abrechnungsjahr,y=total),size=2)+scale_y_continuous(limits=c(0,max(co2_MFH_lintrend$total)))+annotate(geom="text",label=paste0(b1,"x"," + ", b0),x=2008,y=3500,size=6)+theme_bw()+labs(x="Jahr",y="kilo t.")+theme(axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"))+scale_x_continuous(breaks=seq(2002,2018,2))


```



************


\textcolor{black}{Berlin, Wohngebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_ALL_cumsums , "Jahr" , "kilo t." , NULL)
plot_byET(approximate_by_kNN(co2_ALL_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```



************


\textcolor{black}{Berlin, Wohngebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_ALL_rel_cumsums , "Jahr" , "Anteile" , NULL)
plot_byET(approximate_by_kNN(co2_ALL_rel_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```




************


\textcolor{black}{Berlin, Wohngebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}



```{r}
co2_ALL_lintrend <- co2_ALL[, c("abrechnungsjahr","total")]
lin_co2 <- lm(total~abrechnungsjahr , data = co2_ALL)
co2_ALL_lintrend$total <- predict(lin_co2 , newdata = co2_ALL_lintrend)
b0 <- round(as.numeric(lin_co2$coefficients[1]),0)
b1 <- round(as.numeric(lin_co2$coefficients[2]),2)
ggplot()+geom_line(data=co2_ALL_lintrend,aes(x=abrechnungsjahr,y=total),size=2)+scale_y_continuous(limits=c(0,max(co2_ALL_lintrend$total)))+annotate(geom="text",label=paste0(b1,"x"," + ", b0),x=2008,y=4500,size=6)+theme_bw()+labs(x="Jahr",y="kilo t.")+theme(axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"))+scale_x_continuous(breaks=seq(2002,2018,2))


```



```{r}
detach(package:FNN)
library(gridExtra)
library(grid)
library(gtable)
```



************


\textcolor{black}{Zahlen und Tabellen}

```{r,warning=FALSE}
co2_coeff <- sfh_data$co2_coeff
names(co2_coeff) <- c("Jahr","Erdgas","Wärme","Flüssiggas","Heizöl","Holzpellets","Strom")
t0 <- ttheme_default(base_size = 14,
                     core=list(bg_params=list(fill="white",col="black")),
                     colhead = list(bg_params=list(fill="white",col="black")))
tab01 <- tableGrob(co2_coeff,theme=t0,rows=NULL)
header <- tableGrob(co2_coeff[1 , 1] , theme=t0, rows=NULL, cols="CO2 Koeffizienten (g/kWh)")
jn <- gtable_combine(header[1,],tab01,along=2)
#jn <- tab01
#jn$widths <- rep(5,4)#rep(max(jn$widths),length(jn$widths))
jn$widths <- rep(6,7)
jn$layout[1:2,c("l","r")] <- list(1,7)
grid.newpage()
grid.draw(jn)
#grid.draw(tab01)
```








```{r}
#zahlen <- data.frame(MFH = c(nrow(mfh_data$mannheim_data),
#                             sum(mfh_data$mannheim_data$gebaeude_nutzflaeche),
#                             round(100*sum(mfh_data$mannheim_data$gebaeude_nutzflaeche)/mfh_data$totalArea$areaMFH[17],2)) ,
#                     SFH = c(nrow(sfh_data$mannheim_data),
#                             sum(sfh_data$mannheim_data$gebaeude_nutzflaeche),
#                             round(100*sum(sfh_data$mannheim_data$gebaeude_nutzflaeche)/sfh_data$totalArea$areaSFH[17],2)) ,
#                     Gesamt = c(nrow(mfh_data$mannheim_data)+nrow(sfh_data$mannheim_data),
#                                sum(mfh_data$mannheim_data$gebaeude_nutzflaeche)+sum(sfh_data$mannheim_data$gebaeude_nutzflaeche),
#                                round(100*(sum(mfh_data$mannheim_data$gebaeude_nutzflaeche)+sum(sfh_data$mannheim_data$gebaeude_nutzflaeche))/(mfh_#data$totalArea$areaMFH[17] + sfh_data$totalArea$areaSFH[17]),2)))
#names(zahlen) <- c("Mehrfamiliengebäude" , "1-2 Familiengebäude" , "Gesamt")
#tab01 <- tableGrob(zahlen,theme=ttheme_default(base_size = 14),rows=c("Anzahl","Nutzfläche (q.m.)","Coverage (%)"))
#header <- tableGrob(zahlen[1 , 1] , theme=ttheme_default(base_size = 14), rows=NULL, cols="2002 - 2018")
#jn <- gtable_combine(header[1,],tab01,along=2)
#jn$widths <- rep(6,4)
#jn$layout[1:2,c("l","r")] <- list(2,4)
#grid.newpage()
#grid.draw(jn)

```


************

\textcolor{black}{Zahlen und Tabellen}



```{r}
data_report <- data.frame(a=c(" ",
                             "Stichprobe (2002-2018)",
                             "Anzahl",
                             "Beheizte Nutzflache [AN]",
                             "Grundgesamtheit (2018)",
                             "Anzahl",
                             "Beheizte Nutzflache [AN]",
                             "Abdeckung",
                             "Anzahl",
                             "Beheizte Nutzflache"),
                         b=c("Mehrfamiliengebaeude",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " "),
                         c=c("1-2 Familiengebaeude",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " "),
                         d=c("Gesamt",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " ",
                             " "))
border_colors <- "white"
t0 <- ttheme_default()
t1 <- ttheme_default(core=list(bg_params=list(fill=rep("white",9),col=border_colors )))

#tab01 <- tableGrob(data_report,theme=t1,row=NULL,col=NULL)
#tab01 <- gtable_add_grob(tab01 , 
#                         grobs = rectGrob(gp = gpar(fill=NA,lwd=2)),
#                         t = 1, b = 1 , l = 1 , r = 4)
#add a border:
tab01 <- tableGrob(data_report,theme=t1,row=NULL,col=NULL)
tab01 <- gtable_add_grob(tab01,
        grobs = rectGrob(gp = gpar(fill = NA, lwd = 2)),
        t = 1, b = 10, l = 1, r = 4)

tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 3, b = 4, l = 1, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 1, b = 1, l = 1, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 7, b = 7, l = 1, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(0,"npc"),
            y1 = unit(1,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 1, b = 10, l = 3, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(0,"npc"),
            y1 = unit(1,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 1, b = 10, l = 2, r = 3)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(0,"npc"),
            y1 = unit(1,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 1, b = 10, l = 4, r = 4) #WHATTHEFUCK!!!
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 3, b = 3, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 5, b = 5, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 8, b = 8, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 9, b = 9, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 6, b = 6, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 2, b = 2, l = 2, r = 4)
grid.newpage()
grid.draw(tab01)
```


