---
title: "Making data tables in presentations"
author: "Bhaskar Kamble"
date: "9 Juni 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

It is often necessary in presentations to present certain data in the form of tables. These tables often need to be formatted in certain ways, such as the correct alignment of text, suitable widths for the columns, merging certain rows or columns, highlighting certain cells and so on. For this, the `grid`and `gridExtra` packages are used. Here I want to describe possible ways to use these packages to get correctly formatted tables, and also some problems I ran into for which I don't have a solution yet.


```{r}
library(grid)
library(gridExtra)
library(gtable)
tabla_fin <- rbind(
c("","2015\nabril","2016\nabril","2017\nmarzo","2017\nabril"),
c("Pedidos",-23.3,-13.8,-26,-39),
c("Existencias",7.6,1.2,5.3,10.5),
c("Expectativas",30.7,32.7,28.7,24),
c("ICI",-0.1,5.9,-0.9,-8.5),
c("ICI Desest*",0.4,5.7,-3.2,-6.9))
colnames(tabla_fin) <- tabla_fin[1,]
tabla_fin <- tabla_fin[-1,]
rownames(tabla_fin) <- tabla_fin[,1]
tabla_fin <- tabla_fin[,-1]
print(tabla_fin)
t1 <- ttheme_default(
        core=list(
         fg_params=list(fontface=rep("plain", 6), fontfamily="Calibri",
                      x=1.0, hjust=1.0),
         bg_params = list(
                     fill=c(rep("red",3),"blue","green"),
                     col=c("white","white","white","grey80","grey90"),
                     alpha = rep(1,5))
        ),
        rowhead=list(
         fg_params=list(x=0, hjust=0, fontface="plain", fontfamily="Calibri"),
         bg_params = list(
                     fill=c("white",rep("white",3),"grey80","grey90"),
                     col=c("white","white","white","white","grey80","grey90"),
                     alpha = rep(1,5))
        ),
        colhead=list(
         fg_params=list(fontface="plain",fontfamily="Calibri"),
         bg_params = list(
                     fill="grey70",
                     col="grey70",
                     alpha = rep(1,5))
        )
)
t  <- tableGrob(tabla_fin, theme=t1)
grid.newpage()
grid.draw(t)
```

```{r}
a <- gtable(unit(1:3, c("cm")), unit(5, "cm"))
a
gtable_show_layout(a)

# Add a grob:
rect <- rectGrob(gp = gpar(fill = "black"))
a <- gtable_add_grob(a, rect, 1, 1)
a
plot(a)
```


```{r}
library(ggplot2)
p1 <- qplot(mpg, wt, data = mtcars, colour = cyl)
p2 <- qplot(mpg, data = mtcars) + ggtitle("title")
p3 <- qplot(mpg, data = mtcars, geom = "dotplot")
p4 <-
  p1 + facet_wrap( ~ carb, nrow = 1) + theme(legend.position = "none") +
  ggtitle("facetted plot")
```

```{r}
grid.arrange(p1, p2, nrow = 1)
```

```{r}
#https://stackoverflow.com/questions/36454028/how-do-i-customize-particular-columns-for-a-tablegrob-in-r
library(grid)
library(gridExtra)

df <- data.frame(Order = c(1:5),
                 Name = c("Adam", "Ben", "Charlie" , "Ted", "Eddie"), 
                 Score = c(4, 8, 9 , 2 , 6))

#hj <- matrix(c(0, 0.5, 1), ncol=3, nrow=nrow(df), byrow=TRUE)
#x <- matrix(c(0, 0.5, 1), ncol=3, nrow=nrow(df), byrow=TRUE)

hj <- rep(c(0,0.5,1),each=5)
x <- rep(c(0,0.5,1),each=5)

tt1 <- ttheme_default(core=list(fg_params=list(hjust = hj, 
                                               x = x)),
                      colhead=list(fg_params=list(hjust=1, x=0.95)))


dfGrob <- tableGrob(df, rows = NULL, theme = tt1)
grid.newpage()
grid.draw(dfGrob)
```

```{r}
hj <- matrix(c(0, 0.5, 1), ncol=3, nrow=nrow(df), byrow=TRUE)
x <- matrix(c(0, 0.5, 1), ncol=3, nrow=nrow(df), byrow=TRUE)
as.vector(x)
```

For grid package:

https://bookdown.org/rdpeng/RProgDA/the-grid-package.html


```{r}
header_justify <- c(0,0.5,0.5,0.5)
header_x       <- c(0,0.5,0.5,0.5)
core_justify <-   rep(c(0,0.5,0.5,0.5),each=5)
core_x       <-   rep(c(0,0.5,0.5,0.5),each=5)
t_header <- ttheme_default(base_size = 8,
                           colhead=list(fg_params=list(hjust = header_justify , x = header_x)))
t_core   <- ttheme_default(base_size = 8,
                           core=list(fg_params=list(hjust = core_justify , x = core_x)))
daf <- data.frame(SomeLetters = paste0(letters[sample(1:26 , 5)],letters[sample(1:26 , 5)],letters[sample(1:26 , 5)]), 
                  SomeNumbers1 = sample(1:26,5) , 
                  SomeNumbers2 = sample(1:26,5) , 
                  SomeNumbers3 = sample(1:26,5))
tab01 <- tableGrob(daf , theme = t_core , rows=NULL, cols = NULL)
header01 <- tableGrob(daf[1,1:4],theme=t_header,
                      rows=NULL,cols= c("1. Some Letters",
                                        "2. Some Numbers",
                                        "3. Some Numbers",
                                        "4. Some Numbers"))
jn <- gtable_combine(header01[1,],tab01,along=2)
jn$layout[1:4 , c("r","l")] <- list(1:4,1:4)
jn$widths <- c(2,2,2,2)
grid.newpage()
grid.draw(jn)
```

hjust = 1 means left aligned. hjust = 0 means right aligned. The default value of x is 0.5. Increasing x will push the text to the right. Hence makes more sense only in left aligned cases. Decreasing x will push text to the left. Hence makes mmore sense only in the right aligned cases.

For left justify, you can do either of the following:
1. hjust = 0 (right justify) with x = 0 (so that the right-justified text will be pushed to the left and become left justified).
2. hjust = 1 (left justify) with x equal to the default calue of 0.5.

Exrercise: Find the corresponding options for right justifying.

Next step: Can you add a common header spanning across all the columns?


```{r}
header_justify <- c(0,0.5,0.5,0.5)
header_x       <- c(0,0.5,0.5,0.5)
core_justify <-   rep(c(0,0.5,0.5,0.5),each=5)
core_x       <-   rep(c(0,0.5,0.5,0.5),each=5)
t_header <- ttheme_default(base_size = 8,
                           colhead=list(fg_params=list(hjust = header_justify , x = header_x)))
t_core   <- ttheme_default(base_size = 8,
                           core=list(fg_params=list(hjust = core_justify , x = core_x)))
daf <- data.frame(SomeLetters = paste0(letters[sample(1:26 , 5)],letters[sample(1:26 , 5)],letters[sample(1:26 , 5)]), 
                  SomeNumbers1 = sample(1:26,5) , 
                  SomeNumbers2 = sample(1:26,5) , 
                  SomeNumbers3 = sample(1:26,5))

tab01 <- tableGrob(daf , theme = t_core , rows=NULL, cols = NULL)
header01 <- tableGrob(daf[1,1:4],theme=t_header,
                      rows=NULL,cols= c("1. Some Letters",
                                        "2. Some Numbers",
                                        "3. Some Numbers",
                                        "4. Some Numbers"))
jn <- gtable_combine(header01[1,],tab01,along=2)
jn$layout[1:4 , c("r","l")] <- list(1:4,1:4)

t_header <- ttheme_default(base_size=8)
header02 <- tableGrob(daf[1,1],rows=NULL,cols="Common header",theme=t_header)
jn <- gtable_combine(header02[1,],jn,along=2)
jn$layout[1:4 , c("r","l")] <- list(1,4)

t_header <- ttheme_default(base_size=8)
header02 <- tableGrob(daf[1,1:2],rows=NULL,cols=c("CH1", "CH2"),theme=t_header)
jn <- gtable_combine(header02[1,],jn,along=2)
jn$layout[1:4 , c("r","l")] <- list(c(1,4),c(3,4))

jn$widths <- c(2,2,3,3)
grid.newpage()
grid.draw(jn)
```





https://cyancey95.github.io/CompBiol_2018/gridExtraPresentation.html
https://cran.r-project.org/web/packages/gridExtra/vignettes/tableGrob.html
https://bookdown.org/rdpeng/RProgDA/the-grid-package.html
https://rdrr.io/cran/gtable/man/gtable.html
https://cran.r-project.org/web/packages/egg/vignettes/Ecosystem.html
https://stackoverflow.com/questions/44418647/tablegrob-formatting
https://stackoverflow.com/questions/39726423/how-to-merge-vertical-cells-in-tablegrob-output-tables-in-r
http://www.flutterbys.com.au/stats/tut/tut5.2.html





#####################

Trying to merge rows:

https://stackoverflow.com/questions/39726423/how-to-merge-vertical-cells-in-tablegrob-output-tables-in-r

```{r}
alphabets <- c(rep("A", 3), rep("B", 3), rep("C",3))
numbers <- c(rep(c(1,2,3), 3))
df1 <- data.frame(alphabets = alphabets,numbers=numbers)

#sounds <- c('','Ayes','','','Bees','','','Cees','')
sounds <- c("Ayes","Bees","Cees")
df2 <- data.frame(sounds = sounds)
t1 <- ttheme_default(core=list(bg_params=list(fill=rep("white",9),col=rep("red",9))))
t2 <- ttheme_default()
tab1 <- tableGrob(df1,theme = t1,row=NULL)
tab2 <- tableGrob(df2,theme = t2,row=NULL)

halign <- gtable_combine(tab2,tab1, along =1)

grid.newpage()
grid.draw(halign)
```



```{r}
halign$layout
```


```{r}
halign$layout[halign$layout$t != 1 &
                halign$layout$l == 1, c("t")] <-
  c(2,5,8,2,5,8)

halign$layout[halign$layout$b != 1  &
                halign$layout$l == 1, c("b")] <-
  c(4,7,10,4,7,10)
grid.newpage()
grid.draw(halign)
```



#######################################################

```{r}
co2_online <- data.frame(a=c(" ",
                             "Stichprobe (2002-2018)",
                             "Anzahl",
                             "Beheizte Nutzflache [AN]",
                             "Grundgesamtheit (2018)",
                             "Anzahl",
                             "Beheizte Nutzflache [AN]",
                             "Abdeckung",
                             "Anzahl",
                             "Beheizte Nutzflache"),
                         b=c("Mehrfamiliengebaeude",
                             " ",
                             "2753",
                             "3842321",
                             " ",
                             " ",
                             "8599644",
                             " ",
                             " ",
                             "44.7"),
                         c=c("1-2 Familiengebaeude",
                             " ",
                             "2581",
                             "487369",
                             " ",
                             " ",
                             "3637082",
                             " ",
                             " ",
                             "13.4"),
                         d=c("Gesamt",
                             " ",
                             "5334",
                             "4329690",
                             " ",
                             " ",
                             "12237677",
                             " ",
                             " ",
                             "35.4"))
                         
```


```{r}
#border_colors_col1 <- c( rep("black",2) , rep("white",2) , "black" , rep("white",2) , "black" , rep("white",2))
#border_colors_col1 <- c("black" , rep("white",3) , "black" , rep("white",2) , "black" , rep("white",2))
#border_colors_col2 <- c( "black" , "white" , rep("black" , 8))
#border_colors_col3 <- c( "black" , "white" , rep("black" , 8))
#border_colors_col4 <- c( "black" , "white" , rep("black" , 8))
#border_colors <- c(border_colors_col1 , border_colors_col2 , border_colors_col3 , border_colors_col4)
border_colors <- "white"
t0 <- ttheme_default()
t1 <- ttheme_default(core=list(bg_params=list(fill=rep("white",9),col=border_colors )))
#grid.newpage()
#grid.draw(tab01)
```

https://cran.r-project.org/web/packages/gridExtra/vignettes/tableGrob.html

```{r}
tab01 <- tableGrob(co2_online,theme=t1,row=NULL,col=NULL)
#tab01 <- gtable_add_grob(tab01 , 
#                         grobs = rectGrob(gp = gpar(fill=NA,lwd=2)),
#                         t = 1, b = 1 , l = 1 , r = 4)
#add a border:
tab01 <- tableGrob(co2_online,theme=t1,row=NULL,col=NULL)
tab01 <- gtable_add_grob(tab01,
        grobs = rectGrob(gp = gpar(fill = NA, lwd = 2)),
        t = 1, b = 10, l = 1, r = 4)

tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 3, b = 4, l = 1, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 1, b = 1, l = 1, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 7, b = 7, l = 1, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(0,"npc"),
            y1 = unit(1,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 1, b = 10, l = 3, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(0,"npc"),
            y1 = unit(1,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 1, b = 10, l = 2, r = 3)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(0,"npc"),
            y1 = unit(1,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 1, b = 10, l = 4, r = 4) #WHATTHEFUCK!!!
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 3, b = 3, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 5, b = 5, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 8, b = 8, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 9, b = 9, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 6, b = 6, l = 2, r = 4)
tab01 <- gtable_add_grob(tab01,
        grobs = segmentsGrob(
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 1.0,col="black")),
        t = 2, b = 2, l = 2, r = 4)
grid.newpage()
grid.draw(tab01)
```

```{r}
ttt <- ttheme_default(core=list(bg_params=list(fill="red",col="white" )))
g <- tableGrob(iris[1:4, 1:3],theme=ttt)
g <- gtable_add_grob(g,
        grobs = segmentsGrob( # line across the bottom
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 2.0,col="black")),
        t = 3, b = 3, l = 3, r = 3)
grid.newpage()
grid.draw(g)
```



###############################

```{r}
daf <- data.frame(a=1:8 , b = 9:16 , c = 17:24)
tab01 <- tableGrob(daf , theme= t0,row=NULL,col=NULL)
header01 <- tableGrob(daf[1,1],rows=NULL,cols="some text")
jn <- gtable_combine(header01[1,] , tab01 , along = 2)
jn$layout[1:2 , c("r","l")] <- list(1,3)
header02 <- tableGrob(daf[1,1:3],rows=NULL,cols=c("aa","bb","cc"))
jn <- gtable_combine(header02[1,] , jn , along = 2)
jn$layout[1:3 , c("r","l")] <- list(1:3,1:3)
daf2 <- data.frame(d = c("one" , "two" , "three "))
tab02 <- tableGrob(daf2 , theme = t0,  row=NULL)
#jn <- gtable_combine(tab02 , jn )
#jn$layout[, c("t")] <- c(1,2,5,8,1,2,5,8)
#jn$layout[, c("b")] <- c(1,4,7,10,1,4,7,10)
#jn$layout[jn$layout$t != 1 & jn$layout$l == 1, c("t")] <- rep(c(2,5,8),2)
#jn$layout[jn$layout$b != 1 & jn$layout$l == 1, c("b")] <- rep(c(4,7,10),2)
grid.newpage()
grid.draw(jn)
```