---
title: "Making data tables in presentations"
author: "Bhaskar Kamble"
date: "9 Juni 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

It is often necessary in presentations to present certain data in the form of tables. These tables often need to be formatted in certain ways, such as the correct alignment of text, suitable widths for the columns, merging certain rows or columns, highlighting certain cells and so on. For this, the `grid`and `gridExtra` packages are used. Here I want to describe possible ways to use these packages to get correctly formatted tables, and also some problems I ran into for which I don't have a solution yet.


```{r}
library(grid)
library(gridExtra)
library(gtable)
tabla_fin <- rbind(
c("","2015\nabril","2016\nabril","2017\nmarzo","2017\nabril"),
c("Pedidos",-23.3,-13.8,-26,-39),
c("Existencias",7.6,1.2,5.3,10.5),
c("Expectativas",30.7,32.7,28.7,24),
c("ICI",-0.1,5.9,-0.9,-8.5),
c("ICI Desest*",0.4,5.7,-3.2,-6.9))
colnames(tabla_fin) <- tabla_fin[1,]
tabla_fin <- tabla_fin[-1,]
rownames(tabla_fin) <- tabla_fin[,1]
tabla_fin <- tabla_fin[,-1]
print(tabla_fin)
t1 <- ttheme_default(
        core=list(
         fg_params=list(fontface=rep("plain", 6), fontfamily="Calibri",
                      x=1.0, hjust=1.0),
         bg_params = list(
                     fill=c(rep("red",3),"blue","green"),
                     col=c("white","white","white","grey80","grey90"),
                     alpha = rep(1,5))
        ),
        rowhead=list(
         fg_params=list(x=0, hjust=0, fontface="plain", fontfamily="Calibri"),
         bg_params = list(
                     fill=c("white",rep("white",3),"grey80","grey90"),
                     col=c("white","white","white","white","grey80","grey90"),
                     alpha = rep(1,5))
        ),
        colhead=list(
         fg_params=list(fontface="plain",fontfamily="Calibri"),
         bg_params = list(
                     fill="grey70",
                     col="grey70",
                     alpha = rep(1,5))
        )
)
t  <- tableGrob(tabla_fin, theme=t1)
grid.newpage()
grid.draw(t)
```

```{r}
a <- gtable(unit(1:3, c("cm")), unit(5, "cm"))
a
gtable_show_layout(a)

# Add a grob:
rect <- rectGrob(gp = gpar(fill = "black"))
a <- gtable_add_grob(a, rect, 1, 1)
a
plot(a)
```


```{r}
library(ggplot2)
p1 <- qplot(mpg, wt, data = mtcars, colour = cyl)
p2 <- qplot(mpg, data = mtcars) + ggtitle("title")
p3 <- qplot(mpg, data = mtcars, geom = "dotplot")
p4 <-
  p1 + facet_wrap( ~ carb, nrow = 1) + theme(legend.position = "none") +
  ggtitle("facetted plot")
```

```{r}
grid.arrange(p1, p2, nrow = 1)
```

```{r}
#https://stackoverflow.com/questions/36454028/how-do-i-customize-particular-columns-for-a-tablegrob-in-r
library(grid)
library(gridExtra)

df <- data.frame(Order = c(1:5),
                 Name = c("Adam", "Ben", "Charlie" , "Ted", "Eddie"), 
                 Score = c(4, 8, 9 , 2 , 6))

#hj <- matrix(c(0, 0.5, 1), ncol=3, nrow=nrow(df), byrow=TRUE)
#x <- matrix(c(0, 0.5, 1), ncol=3, nrow=nrow(df), byrow=TRUE)

hj <- rep(c(0,0.5,1),each=5)
x <- rep(c(0,0.5,1),each=5)

tt1 <- ttheme_default(core=list(fg_params=list(hjust = hj, 
                                               x = x)),
                      colhead=list(fg_params=list(hjust=1, x=0.95)))


dfGrob <- tableGrob(df, rows = NULL, theme = tt1)
grid.newpage()
grid.draw(dfGrob)
```

```{r}
hj <- matrix(c(0, 0.5, 1), ncol=3, nrow=nrow(df), byrow=TRUE)
x <- matrix(c(0, 0.5, 1), ncol=3, nrow=nrow(df), byrow=TRUE)
as.vector(x)
```

For grid package:

https://bookdown.org/rdpeng/RProgDA/the-grid-package.html


```{r}
header_justify <- c(0,0.5,0.5,0.5)
header_x       <- c(0,0.5,0.5,0.5)
core_justify <-   rep(c(0,0.5,0.5,0.5),each=5)
core_x       <-   rep(c(0,0.5,0.5,0.5),each=5)
t_header <- ttheme_default(base_size = 8,
                           colhead=list(fg_params=list(hjust = header_justify , x = header_x)))
t_core   <- ttheme_default(base_size = 8,
                           core=list(fg_params=list(hjust = core_justify , x = core_x)))
```

```{r}
daf <- data.frame(SomeLetters = paste0(letters[sample(1:26 , 5)],letters[sample(1:26 , 5)],letters[sample(1:26 , 5)]), 
                  SomeNumbers1 = sample(1:26,5) , 
                  SomeNumbers2 = sample(1:26,5) , 
                  SomeNumbers3 = sample(1:26,5))
tab01 <- tableGrob(daf , theme = t_core , rows=NULL, cols = NULL)
header01 <- tableGrob(daf[1,1:4],theme=t_header,
                      rows=NULL,cols= c("1. Some Letters",
                                        "2. Some Numbers",
                                        "3. Some Numbers",
                                        "4. Some Numbers"))
jn <- gtable_combine(header01[1,],tab01,along=2)
jn$widths <- c(2,2,2,2)
grid.newpage()
grid.draw(jn)
```

hjust = 1 means left aligned. hjust = 0 means right aligned. The default value of x is 0.5. Increasing x will push the text to the right. Hence makes more sense only in left aligned cases. Decreasing x will push text to the left. Hence makes mmore sense only in the right aligned cases.

For left justify, you can do either of the following:
1. hjust = 0 (right justify) with x = 0 (so that the right-justified text will be pushed to the left and become left justified).
2. hjust = 1 (left justify) with x equal to the default calue of 0.5.

Exrercise: Find the corresponding options for right justifying.

Next step: Can you add a common header spanning across all the columns?