---
title: "CO<sub>2</sub> emissions in Ulm for 1-2FH"

author: "Bhaskar Kamble and Johannes Hengstenberg"

date: "20 Februar 2019"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=FALSE,message=FALSE)
```

The aim of this report is to calculate CO<sub>2</sub> emissions in the city of Ulm, Germany, caused by energy consumption for heating by 1-2FH. The calculations are primarily  based on the data from [co2online](www.co2online.de). Official statistics from Ulm are also used in the calculations. The data from [co2online](www.co2online.de) is available at [my github repo](https://github.com/bhaskar-kamble/co2online_stats) as R-images.

_Notes to myself:_

- _`Wohngebaeude 2002 - 2018.xlsx` - the sheet `result` contains data on areas for each year._

- _the column for `waerme` in the coefficients file refers includes both `fernmaerme`  `nahwaerme`. In practice `nahwaerme` is so insignificant that it is to be neglected._

The structure of this report is as follows:

1. **Preliminary steps**

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 1a. Get the data
  
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 1b. Introduce some functions
  
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 1c. Get weather data and subset the data for Ulm and 1-2FH

2. **Absolute and relative shares of energy split according to energy sources**

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2a. Get the absolute consumption of energy split by energietraeger for each year and convert to wide format

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2b. Get the relative shares of energy consumption of each `energietraeger` per year

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2c. Find the cumulative sums of the relative shares of energy consumption according to energietraeger per year

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2d. Add linear trends to the above cumulative data

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2e. collect parameters of linear models

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2f. Plotting preparations

3. **CO<sub>2</sub> emissions** 

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3a. Find the mean spezifischer verbrauch for each year
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3b. Find the total area in Ulm - New Method from official data
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3c. Find the total energy consumption (total area times spezifischer verbrauch)
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3d. Break up the total energy consumption according to the `energietraegers`
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3e. The CO<sub>2</sub> coefficients
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3f. The CO<sub>2</sub> emissions - coefficients times energy
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3g. total co2 emissions
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3h. co2 emissions according to energietraeger (absolute value):
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3i. relative shares of co2 emissions according to energietraeger

Now the report starts.


## 1. Preliminary steps

_Note to myself:_

- _These calculations come from the `03_linearmodels.R` file in the same folder._

### 1a. Get the data:

The R-image files used here consist of the co2online data and are also available at my github repo.

```{r}
setwd("/home/kbhaskar/CO2ONLINE/co2emissions_github")
load("MFH20022018.RData")
load("SFH20022018.RData")
#In SFH20022018, abrechnungsjahr and verbrauch_gesamt_kwh are character - change then to int and numeric
SFH20022018$abrechnungsjahr <- as.integer(SFH20022018$abrechnungsjahr)
SFH20022018$verbrauch_gesamt_kwh <- gsub("," , "." , SFH20022018$verbrauch_gesamt_kwh)
SFH20022018$verbrauch_gesamt_kwh <- as.numeric(SFH20022018$verbrauch_gesamt_kwh)
SFH20022018$gtype <- "SFH"
MFH20022018$gtype <- "MFH"
```


### 1b. Introduce some functions:

```{r}
find_ET_shares_by_year <- function(inputdata) {
  require(dplyr)
  by_year_ET <- group_by(inputdata,abrechnungsjahr,energietraeger)
  return(as.data.frame(summarize(by_year_ET,sum(verbrauch_gesamt_kwh))))
}

find_et_list <- function(inputdata) {
  ET_list <- unique(inputdata$energietraeger)  
  return(ET_list)
}
subset_data_by_region <- function(inputdata , region) {
  outputdata <- inputdata[inputdata$Landkreis_von_GS == region , ]
  return(outputdata)
}
readweather <- function(filename) {
  weather_data <- read.csv(filename,header=TRUE , sep=";" , dec="," )
  names(weather_data) <- c("Year","wind","sun","bedeckung","temperatur")
  no_of_years <- 17
  if (dim(weather_data)[1] != no_of_years) {
    stop("check number of years in weather data")
  }
  return(weather_data)
}
```

### 1c. Get weather data and subset the data for Ulm and 1-2FH

_This weather data is not used at present_

```{r}
weather_ulm <- readweather("ulm_weather.csv")
ulm_sfh <- subset_data_by_region(SFH20022018,"Ulm")
ulm_sfh$energietraeger[ulm_sfh$energietraeger=="fernwaerme"] <- "waerme"
et_list <- find_et_list(ulm_sfh)
#et_list <- c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom","waermepumpe")
```

## 2. Absolute and relative shares of energy split according to energy sources (`energietraeger`) per year

### 2a. Get the absolute consumption of energy split by energietraeger for each year and convert to wide format

```{r}
#get the data:
ET_shares_by_year <- find_ET_shares_by_year(ulm_sfh)
names(ET_shares_by_year) <- c("abrechnungsjahr" ,"energietraeger" ,"sum_verbrauch_gesamt_kwh")
#change to wide format
detach(package:dplyr)
library(reshape2)
ET_shares_by_year_wide <- dcast(ET_shares_by_year , abrechnungsjahr ~ energietraeger , value.var = "sum_verbrauch_gesamt_kwh")
ET_shares_by_year_wide[is.na(ET_shares_by_year_wide)]=0.0
drop_cols <- "abrechnungsjahr"
ET_shares_by_year_wide$Yearlysum <- rowSums(ET_shares_by_year_wide[ , !(names(ET_shares_by_year_wide) %in% drop_cols)])
ET_shares_by_year_wide
```

### 2b. Get the relative shares of energy consumption of each `energietraeger` per year

```{r}
drop_cols <- c("abrechnungsjahr","Yearlysum")
final_prop_table <- as.data.frame(sapply(ET_shares_by_year_wide[ , !(names(ET_shares_by_year_wide) %in% drop_cols)],function(obj) obj/ET_shares_by_year_wide$Yearlysum))
final_prop_table$abrechnungsjahr <- 2002:2018
```

This is what it looks like:
```{r}
final_prop_table
```

### 2c. Find the cumulative sums of the relative shares of energy consumption according to energietraeger per year

```{r}
final_prop_table <- final_prop_table[,c("waermepumpe","erdgas","waerme","fluessiggas","heizoel","holzpellets","strom","abrechnungsjahr")]
final_prop_table_cumsums <- t(apply(final_prop_table[, !(names(final_prop_table)=="abrechnungsjahr")] 
                                    , 1 , cumsum))
final_prop_table_cumsums <- as.data.frame(final_prop_table_cumsums)
final_prop_table_cumsums$abrechnungsjahr <- final_prop_table$abrechnungsjahr
final_prop_table_cumsums
```

### 2d. Add linear trends to the above cumulative data


```{r}
#final_prop_table_cumsums_omit2018 <- final_prop_table_cumsums[final_prop_table_cumsums$abrechnungsjahr!=2018 , ]
et_list <- names(final_prop_table_cumsums)[names(final_prop_table_cumsums)!="abrechnungsjahr"]
storage <- list()
for (et in et_list) {
  storage[[et]] <- lm(get(et) ~ abrechnungsjahr , data = final_prop_table_cumsums)
}
for (et in et_list) {
  colname <- paste0(et,"_lm")
  final_prop_table_cumsums[[colname]] <- predict(storage[[et]] , newdata = final_prop_table_cumsums)
}#in the predictions, replace any negative numbers by zeros
#final_prop_table_cumsums
```

### 2e. collect parameters of linear models

```{r}
slopes <- NULL
intercepts <- NULL
for (et in et_list) {
  intercepts <- c(intercepts , as.numeric(coefficients(storage[[et]])[1]))
  slopes <- c(slopes , as.numeric(coefficients(storage[[et]])[2]))
}
```

### 2f. Plotting preparations

Define the color scheme:

```{r}
datawide <- final_prop_table_cumsums
col_list <- c("black","royalblue4","orangered1","gray59","orange","blue","olivedrab4")
cols <- c("waermepumpe" = "black",
          "erdgas"      = "royalblue4",
          "waerme"      = "orangered1",
          "fluessiggas" = "gray59",
          "heizoel"     = "orange",
          "holzpellets" = "blue",
          "strom"       = "olivedrab4")
```

Test plot:

```{r}
require(ggplot2)
ggplot()+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+geom_abline(intercept=intercepts[1],slope=slopes[1],colour=col_list[1]
)+geom_abline(intercept=intercepts[2],slope=slopes[2],colour=col_list[2]
)+geom_abline(intercept=intercepts[3],slope=slopes[3],colour=col_list[3]
)+geom_abline(intercept=intercepts[4],slope=slopes[4],colour=col_list[4]
)+geom_abline(intercept=intercepts[5],slope=slopes[5],colour=col_list[5]
)+geom_abline(intercept=intercepts[6],slope=slopes[6],colour=col_list[6]
)+geom_abline(intercept=intercepts[7],slope=slopes[7],colour=col_list[7])+labs(
x="Abrechnungsjahr",y="energy consumption (relative)",title="Ulm, 1-2FH"
)+scale_color_manual(name="legend",values=cols,breaks=rev(
c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom","waermepumpe"))
) + theme_bw()+scale_x_continuous(breaks=seq(2002,2018,2))
```



#### Save some of the graphs
#### Cumulative Energietraeger Anteile, simple line-plot:
```{r}
ggplot()+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+scale_color_manual(name="legend",values=cols,breaks=rev(
c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom","waermepumpe"))) + labs(
x="Abrechnungsjahr",y="energy consumption (relative)",title="Ulm, 1-2FH")+theme_bw(
)+scale_x_continuous(breaks=seq(2002,2018,2))
```

#### Cumulative Energietraeger Anteile, filled plot:
```{r}
ggplot()+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+scale_color_manual(name=" ",values=cols,breaks=rev(
c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom","waermepumpe"))
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[7])),fill=col_list[7]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1])+theme_bw()+ labs(x="Abrechnungsjahr",y="energy consumption (relative)",title="Ulm, 1-2FH"
)+scale_x_continuous(breaks=seq(2002,2018,2))
```




## 3. Now for the CO<sub>2</sub> emissions

### 3a. Find the mean spezifischer verbrauch for each year


**Important point: Take the `witterungsbereinigter spezifischer Verbrauch` in the next iteration instead of the raw numbers. Right I've just taken the raw numbers in the first iteration**


```{r}
# point - take it for the witterungsbereinigt
#ulm_sfh_omit2018 <- ulm_sfh[ulm_sfh$abrechnungsjahr!=2018 , ]
#detach(package:ggplot2)
#detach(package:dplyr)
#detach(package:reshape2)
library(dplyr)
by_year <- group_by(ulm_sfh , abrechnungsjahr)
spz_verbrauch_mean <- as.data.frame(summarize(by_year,mean(verbrauch_gesamt_kwh_spez)))
names(spz_verbrauch_mean) <- c("abrechnungsjahr" , "mean_spz_verberauch")
#nutzflaeche_mean <- as.data.frame(summarize(by_year,mean(gebaeude_nutzflaeche)))
#names(nutzflaeche_mean) <- c("abrechnungsjahr" , "mean_nutzflaeche")
```

```{r}
spz_verbrauch_mean
```






### 3b. Find the total area in Ulm - New Method from official data

`Wohngebaeude 2002 - 2018.xlsx` - the sheet `result` contains data on areas for each year.

```{r}
totalArea <- read.table("wohngebaeude_2002_2018.txt",header=TRUE)
totalArea <- totalArea[ , c("abrechnungsjahr","totArea")]
totalArea
```



### 3c. Find the total energy consumption (total area times spezifischer verbrauch)
```{r}
totalConsumption <- data.frame(abrechnungsjahr = 2002:2018,gesamtVerbrauch = totalArea$totArea*spz_verbrauch_mean$mean_spz_verberauch)
totalConsumption$inTWh <- totalConsumption$gesamtVerbrauch/1e9
totalConsumption
#ggplot()+geom_point(data=totalConsumption,aes(x=abrechnungsjahr,y=gesamtVerbrauch))+theme_bw()+labs(y="Energy consumption in kWh")
#ggplot()+geom_point(data=totalConsumption,aes(x=abrechnungsjahr,y=inTWh))+theme_bw()+labs(y="Energy consumption in TWh")
```

### 3d. Break up the total energy consumption according to the `energietraegers`

The shares are in the `final_prop_table`.



```{r}
#final_prop_table_omit2018 <- final_prop_table[final_prop_table$abrechnungsjahr!=2018 , ]
is_not_year <- names(final_prop_table) != "abrechnungsjahr"
energy_shares_absolute <- totalConsumption$gesamtVerbrauch * final_prop_table[,is_not_year]
energy_shares_absolute$abrechnungsjahr <- 2002:2018
energy_shares_absolute
```


### 3e. The CO<sub>2</sub> coefficients

I'm using the preliminary coefficients from https://www.dropbox.com/s/j63ednj6tmzakou/4.3.2.15.3.%20CO2-Koeffizienten%202018.xlsx?dl=0

I've saved the above as `MunichCO2Koeffizienten.txt`.

```{r}
co2_coeff <- read.table("MunichCO2Koeffizienten.txt",header=TRUE)
names(co2_coeff) <- c("abrechnungsjahr","erdgas","waerme","fluessiggas","heizoel","holzpellets","strom")
co2_coeff
```

The units for the above coefficients are $g/kWh$.

### 3f. The CO<sub>2</sub> emissions - coefficients $\times$ energy


```{r}
co2_coeff_subset <- co2_coeff#[ , names(co2_coeff)!="waerme"]
co2_coeff_subset
```

```{r}
names(energy_shares_absolute)
```

```{r}
names(co2_coeff_subset)
```

So you have to multiply the coefficents with the energy consumption:

```{r}
###########multiply coefficients with energy consumption##################
# IT is very important that the names of the variables be the same (not 
#necessarily in the same order, but for example the erdgas in both should 
#be named erdgas, and not erdgas in one and Erdgas in another) in the 
#coefficients file and the consumption (energy_shares_absolute) file
#make same names:
#names(energy_shares_absolute)[names(energy_shares_absolute)=="fernwaerme"] <- "waerme"
#same names made
energy_shares_absolute_matchcoeff <- energy_shares_absolute[,names(co2_coeff_subset)]
energy_shares_absolute_matchcoeff
co2_emissions <- (energy_shares_absolute_matchcoeff[,
          names(energy_shares_absolute_matchcoeff)!="abrechnungsjahr"])*co2_coeff_subset[,names(co2_coeff_subset)!="abrechnungsjahr"]
co2_emissions
```

The above answer is in grams. Divide by 1e9 to get the answer in kilo tonnes.

```{r}
co2_emissions_in_kilo_tons <- co2_emissions/1e9
co2_emissions_in_kilo_tons$abrechnungsjahr <- 2002:2018
co2_emissions_in_kilo_tons$total <- rowSums(co2_emissions_in_kilo_tons[,names(co2_emissions_in_kilo_tons)!="abrechnungsjahr"])
co2_emissions_in_kilo_tons
```








### 3g. Total CO<sub>2</sub> emissions

```{r}
linmod <- lm(data=co2_emissions_in_kilo_tons,formula=total~abrechnungsjahr)
a <- as.numeric(coefficients(linmod)[1])
b <- as.numeric(coefficients(linmod)[2])
if (a<0) {
  asign <- " "
} else {asign <- "+"}
if (b<0) {
  bsign <- " "
} else {bsign <- " "}
ggplot()+geom_line(data=co2_emissions_in_kilo_tons,aes(x=abrechnungsjahr,y=total),color="blue")+geom_point(data=co2_emissions_in_kilo_tons,aes(x=abrechnungsjahr,y=total),color="blue")+theme_bw()+labs(x="Abrechnungsjahr",y="co2 emissions (kilo tonnes)",title="Ulm, 1-2FH")+ylim(0,max(co2_emissions_in_kilo_tons$total))+geom_smooth(method="lm",data=co2_emissions_in_kilo_tons,aes(x=abrechnungsjahr,y=total),se=FALSE)+annotate(geom="text",label=paste0(bsign,as.character(round(b,2)),"x",asign,as.character(round(a,0))),x=2008,y=60)+scale_x_continuous(breaks=seq(2002,2018,2))
#https://stackoverflow.com/questions/15633714/adding-a-regression-line-on-a-ggplot  
#ggsave("total_co2_emission.jpg")
```

### 3h. CO<sub>2</sub> emissions according to energietraeger (absolute value):


```{r}
co2cumsums <- co2_emissions_in_kilo_tons
#co2cumsums <- co2cumsums[,c("abrechnungsjahr","holzpellets","strom","fluessiggas","erdgas","heizoel")]
co2cumsums <- as.data.frame(t(apply(co2cumsums[,!(names(co2cumsums)%in%c("abrechnungsjahr","total"))],1,cumsum)))
co2cumsums$abrechnungsjahr <- 2002:2018
co2cumsums
```

##### simple line curve:

```{r}
ggplot()+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+scale_color_manual(name="legend",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))) + labs(x="Abrechnungsjahr",y="co2 emissions (kilo tonnes)",title="Ulm, 1-2FH")+theme_bw()+scale_x_continuous(breaks=seq(2002,2018,2))
```

##### filled graph:

```{r}
ggplot()+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+scale_color_manual(name=" ",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[7])),fill=col_list[7]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="co2 emissions (kilo tonnes)",title="Ulm, 1-2FH")+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_absolute.jpg")
```

### 3i. relative shares of CO<sub>2</sub> emissions according to energietraeger

**do the witterungsbereinigung later. 1. first address these issues: Area in 2018 (see email from Johannes) and 2. the skype chat regarding waerme, fernwaerme and nahwaerme and 3. linearizing the graphs**

```{r}
co2anteile_cumsums <- as.data.frame(sapply(co2cumsums[,names(co2cumsums)!="abrechnungsjahr"] , function(obj) obj/co2cumsums$strom))
co2anteile_cumsums$abrechnungsjahr <- 2002:2018
co2anteile_cumsums
```

```{r}
ggplot()+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+scale_color_manual(name=" ",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[7])),fill=col_list[7]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="co2 emissions (relative)",title="Ulm, 1-2FH")+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_relative.jpg")
```

### changing the order of items in the legend:

```{r}
ggplot()+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+scale_color_manual(name=" ",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[7])),fill=col_list[7]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="co2 emissions (relative)",title="Ulm, 1-2FH")+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("04_co2emissions_proportions_rawdata.jpg")
```

# Make linear trends

- for co2 emissions absolute and relative. 

- show both the points and linear fits for the absolute in one graph and relative in another. 

- Then show the fills for the linear trends- one in absolute and one in relative

`co2anteile_cumsums` and `co2cumsums`
```{r}
co2cumsums
co2anteile_cumsums
```

```{r}
#co2cumsums
#co2anteile_cumsums
et_list_2 <- names(co2cumsums)[names(co2cumsums)!="abrechnungsjahr"]
co2cumsums_linear <- co2cumsums
storage_co2 <- list()
for (et in et_list_2) {
  storage_co2[[et]] <- lm(get(et) ~ abrechnungsjahr , data = co2cumsums)
}
for (et in et_list_2) {
  #colname <- paste0(et,"_lm")
  co2cumsums_linear[[et]] <- predict(storage_co2[[et]] , newdata = co2cumsums)
}


storage_co2_anteile <- list()
co2anteile_cumsums_linear <- co2anteile_cumsums
for (et in et_list_2) {
  storage_co2_anteile[[et]] <- lm(get(et) ~ abrechnungsjahr , data = co2anteile_cumsums)
}
for (et in et_list_2) {
  #colname <- paste0(et,"_lm")
  co2anteile_cumsums_linear[[et]] <- predict(storage_co2_anteile[[et]] , newdata = co2anteile_cumsums)
}
```


```{r}
slopes_co2 <- NULL
intercepts_co2 <- NULL
for (et in et_list_2) {
  intercepts_co2 <- c(intercepts_co2 , as.numeric(coefficients(storage_co2[[et]])[1]))
  slopes_co2     <-     c(slopes_co2 , as.numeric(coefficients(storage_co2[[et]])[2]))
}
slopes_co2_anteile <- NULL
intercepts_co2_anteile <- NULL
for (et in et_list_2) {
  intercepts_co2_anteile <- c(intercepts_co2_anteile , as.numeric(coefficients(storage_co2_anteile[[et]])[1]))
  slopes_co2_anteile     <- c(slopes_co2_anteile , as.numeric(coefficients(storage_co2_anteile[[et]])[2]))
}
```



```{r}
require(ggplot2)
ggplot()+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+geom_abline(intercept=intercepts_co2[1],slope=slopes_co2[1],colour=col_list[2]
)+geom_abline(intercept=intercepts_co2[2],slope=slopes_co2[2],colour=col_list[3]
)+geom_abline(intercept=intercepts_co2[3],slope=slopes_co2[3],colour=col_list[4]
)+geom_abline(intercept=intercepts_co2[4],slope=slopes_co2[4],colour=col_list[5]
)+geom_abline(intercept=intercepts_co2[5],slope=slopes_co2[5],colour=col_list[6]
)+geom_abline(intercept=intercepts_co2[6],slope=slopes_co2[6],colour=col_list[7]
)+labs(x="Abrechnungsjahr",y="co2 emissions (kilo tonnes)"
)+scale_color_manual(name=" ",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))) + theme_bw()+scale_x_continuous(breaks=seq(2002,2018,2))
ggsave("co2emissions_absolute_real_and_linearized.jpg")
```


```{r}
require(ggplot2)
ggplot()+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+geom_abline(intercept=intercepts_co2_anteile[1],slope=slopes_co2_anteile[1],colour=col_list[2]
)+geom_abline(intercept=intercepts_co2_anteile[2],slope=slopes_co2_anteile[2],colour=col_list[3]
)+geom_abline(intercept=intercepts_co2_anteile[3],slope=slopes_co2_anteile[3],colour=col_list[4]
)+geom_abline(intercept=intercepts_co2_anteile[4],slope=slopes_co2_anteile[4],colour=col_list[5]
)+geom_abline(intercept=intercepts_co2_anteile[5],slope=slopes_co2_anteile[5],colour=col_list[6]
)+geom_abline(intercept=intercepts_co2_anteile[6],slope=slopes_co2_anteile[6],colour=col_list[7]
)+labs(x="Abrechnungsjahr",y="co2 emissions (relative)"
)+scale_color_manual(name=" ",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))) + theme_bw()+scale_x_continuous(breaks=seq(2002,2018,2))
ggsave("co2emissions_absolute_real_and_linearized.jpg")
```












## Graph of linear trends of absolute CO<sub>2</sub> emissions:

```{r}
ggplot()+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+scale_color_manual(name=" ",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[7])),fill=col_list[7]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="linearized co2 emissions (kilo tonnes)",title="Ulm, 1-2FH")+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_absolute_linearized.jpg")
```

## Graph of linear trends of relative CO<sub>2</sub> emissions:

```{r}
ggplot()+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[7]),color=et_list[7])
)+scale_color_manual(name=" ",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[7])),fill=col_list[7]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="linearized co2 emissions (relative)",title="Ulm, 1-2FH")+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_relative_linearized.jpg")
```

https://ggplot2.tidyverse.org/reference/scale_manual.html
https://stackoverflow.com/questions/14762181/adding-a-y-axis-label-to-secondary-y-axis-in-matplotlib
