---
title: "CO<sub>2</sub> emissions in Ulm for MFH buildings"

author: "Bhaskar Kamble and Johannes Hengstenberg"

date: "20 Februar 2019"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=FALSE,message=FALSE)
```

The aim of this report is to calculate CO<sub>2</sub> emissions in the city of Ulm, Germany, caused by energy consumption for heating by MFH buildings. The calculations are primarily  based on the data from [co2online](www.co2online.de). Official statistics from Ulm are also used in the calculations. The data from [co2online](www.co2online.de) is available at [my github repo](https://github.com/bhaskar-kamble/co2online_stats) as R-images.

_Notes to myself:_

- _`Wohngebaeude 2002 - 2018.xlsx` - the sheet `result` contains data on areas for each year._

- _the column for `waerme` in the coefficients file refers includes both `fernmaerme`  `nahwaerme`. In practice `nahwaerme` is so insignificant that it is to be neglected._

The co2online data consists of data from different households in Germany with information on energy consumption within a specific year (`abrechnungsjahr`) and on the building (area, year of construction, fuel type etc.) Each year has a different sample and the sample size also varies from year to year. To find the CO<sub>2</sub> emissions in Ulm, we first extract the data for Ulm for 1-2FH. For each year we find the relative shares of energy produced by the different fuels. We also have the data for the energy consumed per square kilometer from the co2online data (the specific heat energy consumption). From the official statistics of Ulm we know the total heated surface area for each year. The specific heat energy consumption is multiplied with the total heated area for each year to find the total energy consumption for that. We also know the relative shares of the different fuels from the co2online data, so we know how much energy was produced by the different fuels for that year. For the same amount of energy produced, each fuel produces a different amount of CO<sub>2</sub>. This amount is given by the CO<sub>2</sub> coefficient of that fuel, whose units are kWh/g. Hence, the number of grams of CO<sub>2</sub> produced by a fuel equals the kWh of energy produced times the coefficients. Since the amount of energy produced by each fuel is known, the amount of CO<sub>2</sub> produced can be calculated.

The structure of this report is as follows:

1. **Preliminary steps**

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 1a. Get the data
  
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 1b. Introduce some functions
  
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 1c. Get weather data and subset the data for Ulm and 1-2FH

2. **Absolute and relative shares of energy split according to energy sources**

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2a. Get the absolute consumption of energy split by energietraeger for each year and convert to wide format

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2b. Get the relative shares of energy consumption of each `energietraeger` per year

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2c. Find the cumulative sums of the relative shares of energy consumption according to energietraeger per year

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2d. Add linear trends to the above cumulative data

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2e. collect parameters of linear models

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2f. Plotting preparations

3. **CO<sub>2</sub> emissions** 

    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3a. Find the mean spezifischer verbrauch for each year
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3b. Find the total area in Ulm - New Method from official data
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3c. Find the total energy consumption (total area times spezifischer verbrauch)
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3d. Break up the total energy consumption according to the `energietraegers`
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3e. The CO<sub>2</sub> coefficients
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3f. The CO<sub>2</sub> emissions - coefficients times energy
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3g. total CO<sub>2</sub> emissions
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3h. CO<sub>2</sub> emissions according to energietraeger (absolute value)
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3i. relative shares of CO<sub>2</sub> emissions according to energietraeger
    
    &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 3j. The specific CO<sub>2</sub> emissions (CO<sub>2</sub> emitted per unit surface area)

Now the report starts.


## 1. Preliminary steps

_Note to myself:_

- _These calculations come from the `03_linearmodels.R` file in the same folder._

### 1a. Get the data:

The R-image files used here consist of the co2online data and are also available at my github repo.

```{r}
setwd("/home/kbhaskar/CO2ONLINE/co2emissions_github")
load("MFH20022018_v2.RData")
#load("SFH20022018.RData")
#In SFH20022018, abrechnungsjahr and verbrauch_gesamt_kwh are character - change then to int and numeric
#SFH20022018$abrechnungsjahr <- as.integer(SFH20022018$abrechnungsjahr)
#SFH20022018$verbrauch_gesamt_kwh <- gsub("," , "." , SFH20022018$verbrauch_gesamt_kwh)
#SFH20022018$verbrauch_gesamt_kwh <- as.numeric(SFH20022018$verbrauch_gesamt_kwh)
#SFH20022018$gtype <- "SFH"
MFH20022018$gtype <- "MFH"
```


### 1b. Introduce some functions:

```{r}
find_ET_shares_by_year <- function(inputdata) {
  require(dplyr)
  by_year_ET <- group_by(inputdata,abrechnungsjahr,energietraeger)
  return(as.data.frame(summarize(by_year_ET,sum(verbrauch_gesamt_kwh))))
}

find_et_list <- function(inputdata) {
  ET_list <- unique(inputdata$energietraeger)  
  return(ET_list)
}
subset_data_by_region <- function(inputdata , region) {
  outputdata <- inputdata[inputdata$Landkreis_von_GS == region , ]
  return(outputdata)
}
readweather <- function(filename) {
  weather_data <- read.csv(filename,header=TRUE , sep=";" , dec="," )
  names(weather_data) <- c("Year","wind","sun","bedeckung","temperatur")
  no_of_years <- 17
  if (dim(weather_data)[1] != no_of_years) {
    stop("check number of years in weather data")
  }
  return(weather_data)
}
```

### 1c. Get weather data and subset the data for Ulm and MFH

_This weather data is not used at present_

```{r}
weather_ulm <- readweather("ulm_weather.csv")
ulm_mfh <- subset_data_by_region(MFH20022018,"Ulm")
ulm_mfh$energietraeger[ulm_mfh$energietraeger=="fernwaerme"] <- "waerme"
ulm_mfh$energietraeger[ulm_mfh$energietraeger=="nahwaerme"] <- "waerme"
et_list <- find_et_list(ulm_mfh)
et_list
#et_list <- c("heizoel","erdgas","waerme","fluessiggas","holzpellets")
```

A quick look into how many data are there for each year and energietraeger:

```{r}
xtabs(~abrechnungsjahr , data=ulm_mfh)
xtabs(~abrechnungsjahr+energietraeger , data=ulm_mfh)
```

## 2. Absolute and relative shares of energy split according to energy sources (`energietraeger`) per year

### 2a. Get the absolute consumption of energy split by energietraeger for each year and convert to wide format

```{r}
#get the data:
ET_shares_by_year <- find_ET_shares_by_year(ulm_mfh)
names(ET_shares_by_year) <- c("abrechnungsjahr" ,"energietraeger" ,"sum_verbrauch_gesamt_kwh")
#change to wide format
detach(package:dplyr)
library(reshape2)
ET_shares_by_year_wide <- dcast(ET_shares_by_year , abrechnungsjahr ~ energietraeger , value.var = "sum_verbrauch_gesamt_kwh")
ET_shares_by_year_wide[is.na(ET_shares_by_year_wide)]=0.0
drop_cols <- "abrechnungsjahr"
ET_shares_by_year_wide$Yearlysum <- rowSums(ET_shares_by_year_wide[ , !(names(ET_shares_by_year_wide) %in% drop_cols)])
ET_shares_by_year_wide
```

Okay so in this case for Ulm MFH, there is no data for 2017 and this creates an error with the command `final_prop_table$abrechnungsjahr <- 2002:2018` in the following `R` block. Hence I must automatically get the years from the `ET_shares_by_year_wide` dataframe.

*_OTOH, this is a good point to introduce data for the missing years by taking the average. Then all years must be included in `years_for_which_data_exists`_*

```{r}
ignore_missing_years <- TRUE
if (ignore_missing_years) {
  years_for_which_data_exists <- ET_shares_by_year_wide$abrechnungsjahr
} else {
  years_for_which_data_exists <- 2002:2018
  #ET_shares_by_year_wide - fill in missing years by the mean
  years_present <- ET_shares_by_year_wide$abrechnungsjahr
  years_absent <- years_for_which_data_exists[!(years_for_which_data_exists %in% years_present)]
  
  for (y in years_absent) {
    dtemp <- c(y,colMeans(ET_shares_by_year_wide[ , names(ET_shares_by_year_wide)!="abrechnungsjahr"]) )
    ET_shares_by_year_wide <- rbind(ET_shares_by_year_wide , dtemp)
    #df1 <- df1[order(df1$year) , ]
  }
  ET_shares_by_year_wide <- ET_shares_by_year_wide[order(ET_shares_by_year_wide$abrechnungsjahr) , ]
}
ET_shares_by_year_wide
```


### 2b. Get the relative shares of energy consumption of each `energietraeger` per year

```{r}
drop_cols <- c("abrechnungsjahr","Yearlysum")
final_prop_table <- as.data.frame(sapply(ET_shares_by_year_wide[ , !(names(ET_shares_by_year_wide) %in% drop_cols)],function(obj) obj/ET_shares_by_year_wide$Yearlysum))
final_prop_table$abrechnungsjahr <- years_for_which_data_exists
```

This is what it looks like:
```{r}
final_prop_table
```



### 2c. Find the cumulative sums of the relative shares of energy consumption according to energietraeger per year

```{r}
final_prop_table <- final_prop_table[,c("erdgas","waerme","fluessiggas","heizoel","holzpellets","abrechnungsjahr")]
final_prop_table_cumsums <- t(apply(final_prop_table[, !(names(final_prop_table)=="abrechnungsjahr")] 
                                    , 1 , cumsum))
final_prop_table_cumsums <- as.data.frame(final_prop_table_cumsums)
final_prop_table_cumsums$abrechnungsjahr <- final_prop_table$abrechnungsjahr
final_prop_table_cumsums
```

### 2d. Add linear trends to the above cumulative data


```{r}
et_list <- names(final_prop_table_cumsums)[names(final_prop_table_cumsums)!="abrechnungsjahr"]
storage <- list()
for (et in et_list) {
  storage[[et]] <- lm(get(et) ~ abrechnungsjahr , data = final_prop_table_cumsums)
}
for (et in et_list) {
  colname <- paste0(et,"_lm")
  final_prop_table_cumsums[[colname]] <- predict(storage[[et]] , newdata = final_prop_table_cumsums)
}#in the predictions, replace any negative numbers by zeros
#final_prop_table_cumsums
```

### 2e. collect parameters of linear models

```{r}
slopes <- NULL
intercepts <- NULL
for (et in et_list) {
  intercepts <- c(intercepts , as.numeric(coefficients(storage[[et]])[1]))
  slopes <- c(slopes , as.numeric(coefficients(storage[[et]])[2]))
}
```

### 2f. Plotting preparations

Define the color scheme and plot title:

```{r}
datawide <- final_prop_table_cumsums
col_list <- c("royalblue4","orangered1","gray59","orange","blue")
cols <- c(
          "erdgas"      = "royalblue4",
          "waerme"      = "orangered1",
          "fluessiggas" = "gray59",
          "heizoel"     = "orange",
          "holzpellets" = "blue"
          )
plot_title <- "Ulm, MFH"
order_legend <- rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets"))
```

Test plot:

```{r}
require(ggplot2)
ggplot()+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_point(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_abline(intercept=intercepts[1],slope=slopes[1],colour=col_list[1]
)+geom_abline(intercept=intercepts[2],slope=slopes[2],colour=col_list[2]
)+geom_abline(intercept=intercepts[3],slope=slopes[3],colour=col_list[3]
)+geom_abline(intercept=intercepts[4],slope=slopes[4],colour=col_list[4]
)+geom_abline(intercept=intercepts[5],slope=slopes[5],colour=col_list[5])+labs(
x="Abrechnungsjahr",y="energy consumption (relative)",title=plot_title
)+scale_color_manual(name="legend",values=cols,breaks=order_legend
) + theme_bw()+scale_x_continuous(breaks=seq(2002,2018,2))
```



#### Save some of the graphs
#### Cumulative Energietraeger Anteile, simple line-plot:
```{r}
ggplot()+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+scale_color_manual(name="legend",values=cols,breaks=order_legend) + labs(
x="Abrechnungsjahr",y="energy consumption (relative)",title=plot_title)+theme_bw(
)+scale_x_continuous(breaks=seq(2002,2018,2))
```

#### Cumulative Energietraeger Anteile, filled plot:
```{r}
ggplot()+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=datawide,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+scale_color_manual(name=" ",values=cols,breaks=order_legend
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+geom_ribbon(data=datawide,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1])+theme_bw()+ labs(x="Abrechnungsjahr",y="energy consumption (relative)",title=plot_title
)+scale_x_continuous(breaks=seq(2002,2018,2))
```




## 3. Now for the CO<sub>2</sub> emissions

### 3a. Find the mean spezifischer verbrauch for each year


**Important point: Take the `witterungsbereinigter spezifischer Verbrauch` in the next iteration instead of the raw numbers. Right I've just taken the raw numbers in the first iteration**


```{r}
# point - take it for the witterungsbereinigt
#ulm_sfh_omit2018 <- ulm_sfh[ulm_sfh$abrechnungsjahr!=2018 , ]
#detach(package:ggplot2)
#detach(package:dplyr)
#detach(package:reshape2)
library(dplyr)
by_year <- group_by(ulm_mfh , abrechnungsjahr)
spz_verbrauch_mean <- as.data.frame(summarize(by_year,mean(verbrauch_gesamt_kwh_spez)))
names(spz_verbrauch_mean) <- c("abrechnungsjahr" , "mean_spz_verberauch")
#nutzflaeche_mean <- as.data.frame(summarize(by_year,mean(gebaeude_nutzflaeche)))
#names(nutzflaeche_mean) <- c("abrechnungsjahr" , "mean_nutzflaeche")
```

```{r}
spz_verbrauch_mean
```






### 3b. Find the total area in Ulm - New Method from official data

`Wohngebaeude 2002 - 2018.xlsx` - the sheet `result` contains data on areas for each year. I saved this file as `Ulm_wohngebaeude_zahl_flaeche.csv`.

```{r}
totalArea <- read.csv("Ulm_wohngebaeude_zahl_flaeche.csv",sep=";")
totalArea <- totalArea[ , c("Year","Flaeche_MFH")]
names(totalArea) <-  c("abrechnungsjahr","totArea")
totalArea <- totalArea[totalArea$abrechnungsjahr %in% years_for_which_data_exists , ]
totalArea
```



### 3c. Find the total energy consumption (total area times spezifischer verbrauch)
```{r}
totalConsumption <- data.frame(abrechnungsjahr = years_for_which_data_exists , gesamtVerbrauch = totalArea$totArea*spz_verbrauch_mean$mean_spz_verberauch)
totalConsumption$inTWh <- totalConsumption$gesamtVerbrauch/1e9
totalConsumption
#ggplot()+geom_point(data=totalConsumption,aes(x=abrechnungsjahr,y=gesamtVerbrauch))+theme_bw()+labs(y="Energy consumption in kWh")
#ggplot()+geom_point(data=totalConsumption,aes(x=abrechnungsjahr,y=inTWh))+theme_bw()+labs(y="Energy consumption in TWh")
```

### 3d. Break up the total energy consumption according to the `energietraegers`

The shares are in the `final_prop_table`.



```{r}
#final_prop_table_omit2018 <- final_prop_table[final_prop_table$abrechnungsjahr!=2018 , ]
is_not_year <- names(final_prop_table) != "abrechnungsjahr"
energy_shares_absolute <- totalConsumption$gesamtVerbrauch * final_prop_table[,is_not_year]
energy_shares_absolute$abrechnungsjahr <- years_for_which_data_exists
energy_shares_absolute
```


### 3e. The CO<sub>2</sub> coefficients

I'm using the preliminary coefficients from https://www.dropbox.com/s/j63ednj6tmzakou/4.3.2.15.3.%20CO2-Koeffizienten%202018.xlsx?dl=0

I've saved the above as `MunichCO2Koeffizienten.txt`.

```{r}
co2_coeff <- read.table("UlmCO2Koeffizienten.txt",header=TRUE)
names(co2_coeff) <- c("abrechnungsjahr","erdgas","waerme","fluessiggas","heizoel","holzpellets","strom")
co2_coeff
```

The units for the above coefficients are $g/kWh$.

### 3f. The CO<sub>2</sub> emissions - coefficients $\times$ energy

```{r}
names(co2_coeff)
names(energy_shares_absolute)
```

The names of columns common to `co2_coeff` and `energy_shares_absolute` must be the same. The above command lets you check this. Next, extract only the common columns from `co2_coeff` and retain only the years which are present in the data

```{r}
co2_coeff_subset <- co2_coeff[ , names(co2_coeff) %in% names(energy_shares_absolute)]
co2_coeff_subset <- co2_coeff_subset[co2_coeff_subset$abrechnungsjahr %in% years_for_which_data_exists , ]
co2_coeff_subset
```




An now you have to multiply the coefficents with the energy consumption:

```{r}
###########multiply coefficients with energy consumption##################
# IT is very important that the names of the variables be the same (not 
#necessarily in the same order, but for example the erdgas in both should 
#be named erdgas, and not erdgas in one and Erdgas in another) in the 
#coefficients file and the consumption (energy_shares_absolute) file
#make same names:
#names(energy_shares_absolute)[names(energy_shares_absolute)=="fernwaerme"] <- "waerme"
#same names made
energy_shares_absolute_matchcoeff <- energy_shares_absolute[,names(co2_coeff_subset)]
energy_shares_absolute_matchcoeff
co2_emissions <- (energy_shares_absolute_matchcoeff[,
          names(energy_shares_absolute_matchcoeff)!="abrechnungsjahr"])*co2_coeff_subset[,names(co2_coeff_subset)!="abrechnungsjahr"]
co2_emissions
```

The above answer is in grams. Divide by 1e9 to get the answer in kilo tonnes.

```{r}
co2_emissions_in_kilo_tons <- co2_emissions/1e9
co2_emissions_in_kilo_tons$abrechnungsjahr <- years_for_which_data_exists
co2_emissions_in_kilo_tons$total <- rowSums(co2_emissions_in_kilo_tons[,names(co2_emissions_in_kilo_tons)!="abrechnungsjahr"])
co2_emissions_in_kilo_tons
```








### 3g. Total CO<sub>2</sub> emissions

```{r}
linmod <- lm(data=co2_emissions_in_kilo_tons,formula=total~abrechnungsjahr)
a <- as.numeric(coefficients(linmod)[1])
b <- as.numeric(coefficients(linmod)[2])
if (a<0) {
  asign <- " "
} else {asign <- "+"}
if (b<0) {
  bsign <- " "
} else {bsign <- " "}
ggplot()+geom_line(data=co2_emissions_in_kilo_tons,aes(x=abrechnungsjahr,y=total),color="blue")+geom_point(data=co2_emissions_in_kilo_tons,aes(x=abrechnungsjahr,y=total),color="blue")+theme_bw()+labs(x="Abrechnungsjahr",y="co2 emissions (kilo tonnes)",title=plot_title)+ylim(0,max(co2_emissions_in_kilo_tons$total))+geom_smooth(method="lm",data=co2_emissions_in_kilo_tons,aes(x=abrechnungsjahr,y=total),se=FALSE)+annotate(geom="text",label=paste0(bsign,as.character(round(b,2)),"x",asign,as.character(round(a,0))),x=2008,y=60)+scale_x_continuous(breaks=seq(2002,2018,2))
#https://stackoverflow.com/questions/15633714/adding-a-regression-line-on-a-ggplot  
#ggsave("total_co2_emission.jpg")
```

### 3h. CO<sub>2</sub> emissions according to energietraeger (absolute value):


```{r}
co2cumsums <- co2_emissions_in_kilo_tons
#co2cumsums <- co2cumsums[,c("abrechnungsjahr","holzpellets","strom","fluessiggas","erdgas","heizoel")]
co2cumsums <- as.data.frame(t(apply(co2cumsums[,!(names(co2cumsums)%in%c("abrechnungsjahr","total"))],1,cumsum)))
co2cumsums$abrechnungsjahr <- years_for_which_data_exists
co2cumsums
```

##### simple line curve:

```{r}
ggplot()+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+scale_color_manual(name="legend",values=cols,breaks=order_legend) + labs(x="Abrechnungsjahr",y="co2 emissions (kilo tonnes)",title=plot_title)+theme_bw()+scale_x_continuous(breaks=seq(2002,2018,2))
```

##### filled graph:

```{r}
ggplot()+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+scale_color_manual(name=" ",values=cols,breaks=rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+geom_ribbon(data=co2cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="co2 emissions (kilo tonnes)",title="Ulm, 1-2FH")+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_absolute.jpg")
```

### 3i. relative shares of CO<sub>2</sub> emissions according to energietraeger

**do the witterungsbereinigung later. 1. first address these issues: Area in 2018 (see email from Johannes) and 2. the skype chat regarding waerme, fernwaerme and nahwaerme and 3. linearizing the graphs**



```{r}
co2anteile_cumsums <- as.data.frame(sapply(co2cumsums[,names(co2cumsums)!="abrechnungsjahr"] , function(obj) obj/co2cumsums$holzpellets))
co2anteile_cumsums$abrechnungsjahr <- years_for_which_data_exists
co2anteile_cumsums
```

```{r}
ggplot()+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+scale_color_manual(name=" ",values=cols,breaks=order_legend
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+geom_ribbon(data=co2anteile_cumsums,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="co2 emissions (relative)",title=plot_title)+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_relative.jpg")
```




### 3j. Specific CO<sub>2</sub> emissions

Now we calculate the total CO<sub>2</sub> emissions per square meter for each year in kg/m<sup>2</sup>

```{r}
spez_co2_emission <- data.frame(abrechnungsjahr = years_for_which_data_exists , spez_co2 = 0.001*rowSums(co2_emissions)/totalArea$totArea)
spez_co2_emission
```

```{r}
linmod_spez <- lm(data=spez_co2_emission,formula=spez_co2~abrechnungsjahr)
a_spez <- as.numeric(coefficients(linmod_spez)[1])
b_spez <- as.numeric(coefficients(linmod_spez)[2])
if (a_spez<0) {
  asign_spez <- " "
} else {asign_spez <- "+"}
if (b_spez<0) {
  bsign_spez <- " "
} else {bsign_spez <- " "}
ggplot()+geom_line(data=spez_co2_emission,aes(x=abrechnungsjahr,y=spez_co2),color="blue")+geom_point(
  data=spez_co2_emission,aes(x=abrechnungsjahr,y=spez_co2),color="blue")+theme_bw()+labs(x="Abrechnungsjahr",
  y="co2 emissions (kg/sq. m)",title=plot_title)+ylim(0,max(spez_co2_emission$spez_co2))+geom_smooth(
  method="lm",data=spez_co2_emission,aes(x=abrechnungsjahr,y=spez_co2),se=FALSE)+annotate(
  geom="text",label=paste0(bsign_spez,as.character(round(b_spez,2)),"x",asign_spez,as.character(round(a_spez,0))
  ),x=2008,y=30)+scale_x_continuous(breaks=seq(2002,2018,2))
```




# Make linear trends

- for co2 emissions absolute and relative. 

- show both the points and linear fits for the absolute in one graph and relative in another. 

- Then show the fills for the linear trends- one in absolute and one in relative

`co2anteile_cumsums` and `co2cumsums`
```{r}
co2cumsums
co2anteile_cumsums
```

```{r}
#co2cumsums
#co2anteile_cumsums
et_list_2 <- names(co2cumsums)[names(co2cumsums)!="abrechnungsjahr"]
co2cumsums_linear <- co2cumsums
storage_co2 <- list()
for (et in et_list_2) {
  storage_co2[[et]] <- lm(get(et) ~ abrechnungsjahr , data = co2cumsums)
}
for (et in et_list_2) {
  #colname <- paste0(et,"_lm")
  co2cumsums_linear[[et]] <- predict(storage_co2[[et]] , newdata = co2cumsums)
}


storage_co2_anteile <- list()
co2anteile_cumsums_linear <- co2anteile_cumsums
for (et in et_list_2) {
  storage_co2_anteile[[et]] <- lm(get(et) ~ abrechnungsjahr , data = co2anteile_cumsums)
}
for (et in et_list_2) {
  #colname <- paste0(et,"_lm")
  co2anteile_cumsums_linear[[et]] <- predict(storage_co2_anteile[[et]] , newdata = co2anteile_cumsums)
}
```


```{r}
slopes_co2 <- NULL
intercepts_co2 <- NULL
for (et in et_list_2) {
  intercepts_co2 <- c(intercepts_co2 , as.numeric(coefficients(storage_co2[[et]])[1]))
  slopes_co2     <-     c(slopes_co2 , as.numeric(coefficients(storage_co2[[et]])[2]))
}
slopes_co2_anteile <- NULL
intercepts_co2_anteile <- NULL
for (et in et_list_2) {
  intercepts_co2_anteile <- c(intercepts_co2_anteile , as.numeric(coefficients(storage_co2_anteile[[et]])[1]))
  slopes_co2_anteile     <- c(slopes_co2_anteile , as.numeric(coefficients(storage_co2_anteile[[et]])[2]))
}
```



```{r}
require(ggplot2)
ggplot()+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_point(data=co2cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_abline(intercept=intercepts_co2[1],slope=slopes_co2[1],colour=col_list[1]
)+geom_abline(intercept=intercepts_co2[2],slope=slopes_co2[2],colour=col_list[2]
)+geom_abline(intercept=intercepts_co2[3],slope=slopes_co2[3],colour=col_list[3]
)+geom_abline(intercept=intercepts_co2[4],slope=slopes_co2[4],colour=col_list[4]
)+geom_abline(intercept=intercepts_co2[5],slope=slopes_co2[5],colour=col_list[5]
)+labs(x="Abrechnungsjahr",y="co2 emissions (kilo tonnes)"
)+scale_color_manual(name=" ",values=cols,breaks=order_legend) + theme_bw()+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_absolute_real_and_linearized.jpg")
```


```{r}
require(ggplot2)
ggplot()+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_point(data=co2anteile_cumsums,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+geom_abline(intercept=intercepts_co2_anteile[1],slope=slopes_co2_anteile[1],colour=col_list[1]
)+geom_abline(intercept=intercepts_co2_anteile[2],slope=slopes_co2_anteile[2],colour=col_list[2]
)+geom_abline(intercept=intercepts_co2_anteile[3],slope=slopes_co2_anteile[3],colour=col_list[3]
)+geom_abline(intercept=intercepts_co2_anteile[4],slope=slopes_co2_anteile[4],colour=col_list[4]
)+geom_abline(intercept=intercepts_co2_anteile[5],slope=slopes_co2_anteile[5],colour=col_list[5]
)+labs(x="Abrechnungsjahr",y="co2 emissions (relative)"
)+scale_color_manual(name=" ",values=cols,breaks=order_legend) + theme_bw()+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_absolute_real_and_linearized.jpg")
```












## Graph of linear trends of absolute CO<sub>2</sub> emissions:

```{r}
ggplot()+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+scale_color_manual(name=" ",values=cols,breaks=order_legend
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+geom_ribbon(data=co2cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="linearized co2 emissions (kilo tonnes)",title=plot_title)+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_absolute_linearized.jpg")
```

## Graph of linear trends of relative CO<sub>2</sub> emissions:

```{r}
ggplot()+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
)+geom_line(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
)+scale_color_manual(name=" ",values=cols,breaks=order_legend
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
)+geom_ribbon(data=co2anteile_cumsums_linear,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1]
)+theme_bw()+ labs(x="Abrechnungsjahr",y="linearized co2 emissions (relative)",title=plot_title)+scale_x_continuous(breaks=seq(2002,2018,2))
#ggsave("co2emissions_relative_linearized.jpg")
```

## Save the data

```{r}
write.csv(final_prop_table , file = "./data/ulm/mfh/ET_anteile_verbrauch_mfh.csv") #comes from co2online data
write.csv(spz_verbrauch_mean , file = "./data/ulm/mfh/spz_verbrauch_mfh.csv")      #comes from co2online data
# total area: wohngebaeude_2002_2018.txt contains the total area
write.csv(totalConsumption , file = "./data/ulm/mfh/gesamt_verbrauch_mfh.csv")     #comes from co2online and area data
write.csv(co2_emissions_in_kilo_tons , file = "./data/ulm/mfh/co2_emissions_kilo_tons_mfh.csv") #comes from co2online, coeff. and area data
```

https://ggplot2.tidyverse.org/reference/scale_manual.html
https://stackoverflow.com/questions/14762181/adding-a-y-axis-label-to-secondary-y-axis-in-matplotlib
