---
title: "Report on Bayern CO2 Emissions"
author: "Bhaskar Kamble"
date: "14 August 2020"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    theme: united
    toc_float: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
```

```{r}
path_to_data <- "D:/GITHUB_REPOS/co2emissions/Konstanz/KonstanzData/"
```

```{r, message=FALSE, warning=FALSE}
source("D:/GITHUB_REPOS/co2emissions/Konstanz/mainCO2_konstanz.R")
et_list <- c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom")
```

```{r}
sfh_data <- main_function("SFH" , et_list )
mfh_data <- main_function("MFH" , et_list )
co2_SFH <- sfh_data$co2_emissions#main_function("SFH" , et_list)
co2_MFH <- mfh_data$co2_emissions#main_function("MFH" , et_list)
co2_ALL <- co2_SFH + co2_MFH
co2_ALL$abrechnungsjahr <- 2002:2018
co2_SFH <- co2_SFH/1e9 # in kilo tons
co2_MFH <- co2_MFH/1e9 # in kilo tons
co2_ALL <- co2_ALL/1e9 # in kilo tons
co2_SFH$abrechnungsjahr <- 2002:2018
co2_MFH$abrechnungsjahr <- 2002:2018
co2_ALL$abrechnungsjahr <- 2002:2018
```



```{r}
# You must impute average value of CO2 emissions for Strom for the period 2002-2009.
# Ideally you must impute these missing values to the energy consumption and area covered by Strom in the period 2002-2009.
# anyway do it for co2 emissions now.
# 1. Modify CO2_SFH
# 2. Modify CO2_MFH
# Add them to get CO2_ALL like you did in the first code chunk.
co2_SFH$strom[co2_SFH$abrechnungsjahr < 2010] <- mean(co2_SFH$strom[co2_SFH$abrechnungsjahr >2009])
co2_MFH$strom[co2_MFH$abrechnungsjahr < 2010] <- mean(co2_MFH$strom[co2_MFH$abrechnungsjahr >2009])
co2_ALL <- co2_SFH + co2_MFH
co2_ALL$abrechnungsjahr <- 2002:2018
co2_SFH <- getRowSums(co2_SFH[ , names(co2_SFH)!="total"] , dropCols = "abrechnungsjahr")
co2_MFH <- getRowSums(co2_MFH[ , names(co2_MFH)!="total"] , dropCols = "abrechnungsjahr")
co2_ALL <- getRowSums(co2_ALL[ , names(co2_ALL)!="total"] , dropCols = "abrechnungsjahr")
```


```{r}
co2_MFH_rel <- find_proportions(co2_MFH , c("abrechnungsjahr" , "total"))
co2_MFH_rel <- getRowSums(co2_MFH_rel , "abrechnungsjahr")
co2_SFH_rel <- find_proportions(co2_SFH , c("abrechnungsjahr" , "total"))
co2_SFH_rel <- getRowSums(co2_SFH_rel , "abrechnungsjahr")
co2_ALL_rel <- find_proportions(co2_ALL , c("abrechnungsjahr" , "total"))
co2_ALL_rel <- getRowSums(co2_ALL_rel , "abrechnungsjahr")
```

```{r}
source("D:/GITHUB_REPOS/co2emissions/Berlin/BezirkAnalysis/getCumSums.R")
co2_SFH_cumsums <- getCumSums(co2_SFH , c("abrechnungsjahr","total"))
co2_MFH_cumsums <- getCumSums(co2_MFH , c("abrechnungsjahr","total"))
co2_ALL_cumsums <- getCumSums(co2_ALL , c("abrechnungsjahr","total"))
co2_SFH_rel_cumsums <- getCumSums(co2_SFH_rel , c("abrechnungsjahr","total"))
co2_MFH_rel_cumsums <- getCumSums(co2_MFH_rel , c("abrechnungsjahr","total"))
co2_ALL_rel_cumsums <- getCumSums(co2_ALL_rel , c("abrechnungsjahr","total"))
```


```{r}
#et_list <- names(co2_SFH)[!(names(co2_SFH) %in% c("abrechnungsjahr","total"))]
col_list <- c("royalblue4","orangered1","gray59","orange","blue","olivedrab4")
cols <- c(
          "erdgas"      = "royalblue4",
          "waerme"      = "orangered1",
          "fluessiggas" = "gray59",
          "heizoel"     = "orange",
          "holzpellets" = "blue",
          "strom"       = "olivedrab4"
          )
plot_title <- NULL
order_legend <- rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
order_labels <- rev(c("Erdgas","W?rme (N+F)","Fl?ssiggas","Heiz?l","Holzpellets","Strom (D+WP)"))
```

```{r, message=FALSE, warning=FALSE}
require(ggplot2)
plot_byET <- function(obj,xlabel,ylabel,plottitle) {
  ggplot()+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1]),size=5
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
  )+scale_color_manual(labels=order_labels,name=" ",values=cols,breaks=order_legend
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1])+theme_bw()+ labs(x=xlabel,y=ylabel,title=plottitle) + theme(plot.title=element_text(size=30), axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"), legend.key.size=unit(2, "lines")
  )+scale_x_continuous(breaks=seq(2002,2018,4))
}
```


```{r}
linearizer <- function(obj,dropCols,xVar) {
  obj_new <- obj[ , !(names(obj) %in% dropCols)]
  feature_list <- names(obj_new)[ !(names(obj_new) %in% c(dropCols,xVar)) ]
  storage <- list()
  for (feature in feature_list) {
    storage[[feature]] <- lm(get(feature) ~ get(xVar) , data = obj)
    obj_new[[feature]] <- as.numeric(predict(storage[[feature]] , newdata = obj))
  }
  return(obj_new)
}
j <- 1
```








# 1. 1-2 Family Houses

## 1.1. Sample Size

```{r}
bland_data <- sfh_data$bundesland_data
#dim(bland_data)
data.frame(table(bland_data$abrechnungsjahr))
```


The sample size for SFH buildings is `r nrow(bland_data)`.

## 1.`r (j <- j+1)`. Energy Proportions

```{r}
sfh_data$energy_prop_table
write.csv2(sfh_data$energy_prop_table , file = paste0(path_to_data,"01_SFH_energyProportions.csv"),row.names=FALSE)
```


```{r}
en_props_cum <- getCumSums(sfh_data$energy_prop_table,dropCols="abrechnungsjahr")
#en_props_cum
```

```{r}
plot_byET(en_props_cum,xlabel="Jahr",ylabel="Percentage",plottitle=NULL)
```

## 1.`r (j <- j+1)`. Area proportions

```{r}
sfh_data$area_prop_table
write.csv2(sfh_data$area_prop_table , file =paste0(path_to_data,"02_SFH_areaProportions.csv"),row.names=FALSE)

```

## 1.`r (j <- j+1)`. Total Areas

meter- square

```{r}
sfh_data_area <- sfh_data$totalArea
sfh_data_area
write.csv2(sfh_data$totalArea , file = paste0(path_to_data,"03_SFH_totalArea.csv"),row.names=FALSE)
```

The coverage of SFH buildings is `r sum(bland_data$gebaeude_nutzflaeche)/sfh_data_area$areaSFH[sfh_data_area$abrechnungsjahr==2018]`.



## 1.`r (j <- j+1)`. Mean specific consumption

kWh/m-square

```{r}
sfh_data$spz_verbrauch_mean
write.csv2(sfh_data$spz_verbrauch_mean , file = paste0(path_to_data,"04_SFH_spz_verbrauch_mean.csv"),row.names=FALSE)
```

## 1.`r (j <- j+1)`. Total Consumption

Units: kWh.

```{r}
sfh_data$totalConsumption
write.csv2(sfh_data$totalConsumption , file = paste0(path_to_data,"05_SFH_totalConsumption.csv"),row.names=FALSE)
```

## 1.`r (j <- j+1)`. Energy Shares absolute

These are in kWh.

```{r}
sfh_data$energy_shares_absolute
write.csv2(sfh_data$energy_shares_absolute , file = paste0(path_to_data,"06_SFH_energy_shares_absolute.csv"),row.names=FALSE)
```


## 1.`r (j <- j+1)`. CO2 emissions

The following table gives the answer in kilo tons.

```{r}
co2_SFH
write.csv2(co2_SFH , file = paste0(path_to_data,"07_SFH_co2emissions.csv"),row.names=FALSE)
```

```{r}
plot_byET(co2_SFH_cumsums , xlabel = "Jahr" , ylabel = "kilo tons" , plottitle = NULL)
```



```{r}
co2_SFH_cumsums
```

```{r}
co2_SFH_cumsums_linear <- linearizer(co2_SFH_cumsums , dropCols = NULL , xVar = "abrechnungsjahr")
```


```{r}
plot_byET(co2_SFH_cumsums_linear , xlabel = "Jahr" , ylabel = "kilo tons" , plottitle = NULL)
```














# 2. Multi-Family Houses


## 2.1. Sample Size and coverage

```{r}
bland_data <- mfh_data$bundesland_data
#dim(bland_data)
data.frame(table(bland_data$abrechnungsjahr))
j <- 1
```

```{r}
sum(bland_data$gebaeude_nutzflaeche)
```

The sample size for MFH buildings is `r nrow(bland_data)`.





## 2.`r (j <- j+1)` Energy Proportions

```{r}
mfh_data$energy_prop_table
write.csv2(mfh_data$energy_prop_table , file = paste0(path_to_data,"01_MFH_energyProportions.csv"),row.names=FALSE)
```

## 2.`r (j <- j+1)`. Area proportions

```{r}
mfh_data$area_prop_table
write.csv2(mfh_data$area_prop_table , file = paste0(path_to_data,"02_MFH_areaProportions.csv"),row.names=FALSE)
```

## 2.`r (j <- j+1)`. Total Areas

meter- square

```{r}
mfh_data_area <- mfh_data$totalArea
mfh_data_area
write.csv2(mfh_data$totalArea , file = paste0(path_to_data,"03_MFH_totalArea.csv"),row.names=FALSE)
sum(bland_data$gebaeude_nutzflaeche)/mfh_data_area$areaMFH[mfh_data_area$abrechnungsjahr==2018]
```

The coverage of MFH buildings is `r sum(bland_data$gebaeude_nutzflaeche)/mfh_data_area$areaMFH[mfh_data_area$abrechnungsjahr==2018]`.

## 2.`r (j <- j+1)`. Mean specific consumption

kWh/m-square

```{r}
mfh_data$spz_verbrauch_mean
write.csv2(mfh_data$spz_verbrauch_mean , file = paste0(path_to_data,"04_MFH_spz_verbrauch_mean.csv"),row.names=FALSE)
```

## 2.`r (j <- j+1)`. Total Consumption

Units: kWh.

```{r}
mfh_data$totalConsumption
write.csv2(mfh_data$totalConsumption , file = paste0(path_to_data,"05_MFH_totalConsumption.csv"),row.names=FALSE)
```

## 2.`r (j <- j+1)`. Energy Shares absolute

These are in kWh.

```{r}
mfh_data$energy_shares_absolute
write.csv2(mfh_data$energy_shares_absolute , file = paste0(path_to_data,"06_MFH_energy_shares_absolute.csv"),row.names=FALSE)
```


## 2.`r (j <- j+1)`. CO2 emissions

The following table gives the answer in kilo tons.

```{r}
co2_MFH
write.csv2(co2_MFH , file = paste0(path_to_data,"07_MFH_co2emissions.csv"),row.names=FALSE)
```

```{r}
plot_byET(co2_MFH_cumsums , xlabel = "Jahr" , ylabel = "kilo tons" , plottitle = NULL)
```



```{r}
co2_MFH_cumsums_linear <- linearizer(co2_MFH_cumsums , dropCols = NULL , xVar = "abrechnungsjahr")
```


```{r}
plot_byET(co2_MFH_cumsums_linear , xlabel = "Jahr" , ylabel = "kilo tons" , plottitle = NULL)
```

