---
title: "Mannheim CO$_2$ Emissionen (2002 - 2018)"
author: "Bhaskar Kamble"
date: "4 Juni 2019"
output: 
  beamer_presentation:    
    includes:
      in_header: D:/GITHUB_REPOS/co2emissions/Berlin/BezirkAnalysis/header_pagenrs.tex
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=FALSE,message=FALSE,warning=FALSE)
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
source("D:/GITHUB_REPOS/co2emissions/Mannheim/mainCO2_Mannheim.R")
et_list <- c("erdgas","fluessiggas","heizoel","holzpellets","strom","waerme")

sfh_data <- main_function("SFH" , et_list)
mfh_data <- main_function("MFH" , et_list)


co2_SFH <- sfh_data$co2_emissions#main_function("SFH" , et_list)
co2_MFH <- mfh_data$co2_emissions#main_function("MFH" , et_list)
co2_ALL <- co2_SFH + co2_MFH
co2_ALL$abrechnungsjahr <- 2002:2018
co2_SFH <- co2_SFH/1e9 # in kilo tons
co2_MFH <- co2_MFH/1e9 # in kilo tons
co2_ALL <- co2_ALL/1e9 # in kilo tons
co2_SFH$abrechnungsjahr <- 2002:2018
co2_MFH$abrechnungsjahr <- 2002:2018
co2_ALL$abrechnungsjahr <- 2002:2018
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
co2_MFH_rel <- find_proportions(co2_MFH , c("abrechnungsjahr" , "total"))
co2_MFH_rel <- getRowSums(co2_MFH_rel , "abrechnungsjahr")
co2_SFH_rel <- find_proportions(co2_SFH , c("abrechnungsjahr" , "total"))
co2_SFH_rel <- getRowSums(co2_SFH_rel , "abrechnungsjahr")
co2_ALL_rel <- find_proportions(co2_ALL , c("abrechnungsjahr" , "total"))
co2_ALL_rel <- getRowSums(co2_ALL_rel , "abrechnungsjahr")
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
source("D:/GITHUB_REPOS/co2emissions/Berlin/BezirkAnalysis/getCumSums.R")
co2_SFH_cumsums <- getCumSums(co2_SFH , c("abrechnungsjahr","total"))
co2_MFH_cumsums <- getCumSums(co2_MFH , c("abrechnungsjahr","total"))
co2_ALL_cumsums <- getCumSums(co2_ALL , c("abrechnungsjahr","total"))
co2_SFH_rel_cumsums <- getCumSums(co2_SFH_rel , c("abrechnungsjahr","total"))
co2_MFH_rel_cumsums <- getCumSums(co2_MFH_rel , c("abrechnungsjahr","total"))
co2_ALL_rel_cumsums <- getCumSums(co2_ALL_rel , c("abrechnungsjahr","total"))
```


```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
et_list <- names(co2_SFH)[!(names(co2_SFH) %in% c("abrechnungsjahr","total"))]
col_list <- c("royalblue4","orangered1","gray59","orange","blue","olivedrab4")
cols <- c(
          "erdgas"      = "royalblue4",
          "waerme"      = "orangered1",
          "fluessiggas" = "gray59",
          "heizoel"     = "orange",
          "holzpellets" = "blue",
          "strom"       = "olivedrab4"
          )
plot_title <- NULL
order_legend <- rev(c("erdgas","waerme","fluessiggas","heizoel","holzpellets","strom"))
order_labels <- rev(c("Erdgas","Wärme (N+F)","Flüssiggas","Heizöl","Holzpellets","Strom (D+WP)"))
```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
require(ggplot2)
plot_byET <- function(obj,xlabel,ylabel,plottitle) {
  ggplot()+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[1]),color=et_list[1]),size=5
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[2]),color=et_list[2])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[3]),color=et_list[3])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[4]),color=et_list[4])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[5]),color=et_list[5])
  )+geom_line(data=obj,aes(x=abrechnungsjahr,y=get(et_list[6]),color=et_list[6])
  )+scale_color_manual(labels=order_labels,name=" ",values=cols,breaks=order_legend
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[6])),fill=col_list[6]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[5])),fill=col_list[5]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[4])),fill=col_list[4]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[3])),fill=col_list[3]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[2])),fill=col_list[2]
  )+geom_ribbon(data=obj,aes(x=abrechnungsjahr,ymin=0,ymax=get(et_list[1])),fill=col_list[1])+theme_bw()+ labs(x=xlabel,y=ylabel,title=plottitle) + theme(plot.title=element_text(size=30), axis.title.x=element_text(size=20, face="bold"), axis.title.y=element_text(size=20, face="bold"), legend.text = element_text(size=15), axis.text.x=element_text(size=15,face="bold"), axis.text.y=element_text(size=15,face="bold"), legend.key.size=unit(2, "lines")
  )+scale_x_continuous(breaks=seq(2002,2018,2))
}
```


```{r}
require(FNN)
approximate_by_kNN <- function(obj,no_of_neighbors,year_grid) {
  #obj is the data frame of the cumulative co2 emissions (absolute or relative)
  obj_new <- data.frame(abrechnungsjahr=year_grid)
  for (e in names(obj)[names(obj)!="abrechnungsjahr"]) {
    knnr.out <- knn.reg(train=obj$abrechnungsjahr , test=data.frame(abrechnungsjahr=year_grid) , y=obj[[e]] , k=no_of_neighbors)
    #in the above, test can be a finer grid of the abrechnungsjahr (2002 to 2018 in steps of 0.01, for example). 
    #This is the year_grid argument
    #e is looped over the energietraegers
    obj_new[[e]] <- knnr.out$pred
  }
  return(obj_new)
}
neighbors <- 3
```


#### \textcolor{black}{Mannheim, 1-2 Familiengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_SFH_cumsums , "Jahr" , "kilo t." , NULL)
plot_byET(approximate_by_kNN(co2_SFH_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```




#### \textcolor{black}{Mannheim, 1-2 Familiengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_SFH_rel_cumsums , "Jahr" , "Anteile" , NULL)
plot_byET(approximate_by_kNN(co2_SFH_rel_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```

#### \textcolor{black}{Mannheim, Mehrfamiliengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_MFH_cumsums , "Jahr" , "kilo t." , NULL)
plot_byET(approximate_by_kNN(co2_MFH_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```

#### \textcolor{black}{Mannheim, Mehrfamiliengebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_MFH_rel_cumsums , "Jahr" , "Anteile" , NULL)
plot_byET(approximate_by_kNN(co2_MFH_rel_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```


#### \textcolor{black}{Mannheim, Wohngebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_ALL_cumsums , "Jahr" , "kilo t." , NULL)
plot_byET(approximate_by_kNN(co2_ALL_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```

#### \textcolor{black}{Mannheim, Wohngebäude, CO$_2$ Emissionen aus Beheizung 2002 - 2018}

```{r}
#plot_byET(co2_ALL_rel_cumsums , "Jahr" , "Anteile" , NULL)
plot_byET(approximate_by_kNN(co2_ALL_rel_cumsums,no_of_neighbors=neighbors,seq(2002,2018,1)) , "Jahr" , "kilo t." , NULL)
```



```{r}
detach(package:FNN)
library(gridExtra)
library(grid)
```

#### \textcolor{black}{Zahlen und Tabellen}

```{r}
co2coeff <- data.frame(Erdgas=240,Waerme=244,Fluessiggas=234,heizoel=310,holzpellets=40,strom=500)
names(co2coeff) <- c("Erdgas","Wärme","Flüssiggas","Heizöl","Holzpellets","Strom")
tab01 <- tableGrob(co2coeff,theme=ttheme_default(base_size = 14),rows=NULL)
header <- tableGrob(co2coeff[1 , 1] , theme=ttheme_default(base_size = 14), rows=NULL, cols="CO2 Koeffizienten (g/kWh)")

```

```{r,warning=FALSE}
jn <- gtable_combine(header[1,],tab01,along=2)
#jn <- tab01
#jn$widths <- rep(5,4)#rep(max(jn$widths),length(jn$widths))
jn$widths <- rep(6,6)
jn$layout[1:2,c("l","r")] <- list(1,6)
grid.newpage()
grid.draw(jn)
#grid.draw(tab01)
```






#### \textcolor{black}{Zahlen und Tabellen}

```{r}
zahlen <- data.frame(MFH = c(nrow(mfh_data$mannheim_data),
                             sum(mfh_data$mannheim_data$gebaeude_nutzflaeche),
                             round(100*sum(mfh_data$mannheim_data$gebaeude_nutzflaeche)/mfh_data$totalArea$areaMFH[17],2)) ,
                     SFH = c(nrow(sfh_data$mannheim_data),
                             sum(sfh_data$mannheim_data$gebaeude_nutzflaeche),
                             round(100*sum(sfh_data$mannheim_data$gebaeude_nutzflaeche)/sfh_data$totalArea$areaSFH[17],2)) ,
                     Gesamt = c(nrow(mfh_data$mannheim_data)+nrow(sfh_data$mannheim_data),
                                sum(mfh_data$mannheim_data$gebaeude_nutzflaeche)+sum(sfh_data$mannheim_data$gebaeude_nutzflaeche),
                                round(100*(sum(mfh_data$mannheim_data$gebaeude_nutzflaeche)+sum(sfh_data$mannheim_data$gebaeude_nutzflaeche))/(mfh_data$totalArea$areaMFH[17] + sfh_data$totalArea$areaSFH[17]),2)))
names(zahlen) <- c("Mehrfamiliengebäude" , "1-2 Familiengebäude" , "Gesamt")
tab01 <- tableGrob(zahlen,theme=ttheme_default(base_size = 14),rows=c("Anzahl","Nutzfläche (q.m.)","Coverage (%)"))
header <- tableGrob(zahlen[1 , 1] , theme=ttheme_default(base_size = 14), rows=NULL, cols="2002 - 2018")
jn <- gtable_combine(header[1,],tab01,along=2)
jn$widths <- rep(6,4)
jn$layout[1:2,c("l","r")] <- list(2,4)
grid.newpage()
grid.draw(jn)

```